---
title: "R Notebook"
output: html_notebook
---

## Metadata

Required libraries and runtime environment description.

```{r load_libraries, echo=TRUE, message=FALSE, warning=FALSE}
library(emidata)
library(tidyverse)
library(tidytext)
```


```{r session_info}
devtools::session_info(include_base = TRUE)
```

This document is an EDA notebook to explore descriptive and informative figures of the dataset *papers* in the *emidata* package. Type `?papers` for information. 

## Data 

The data for the analysis is in the *papers* dataset that has `` `r nrow(papers)` `` references.

```{r data_source, echo=TRUE}
papers %>% str()
```

AS part o the text analysis of papers, i.e. wordcloud and terms frequency analysis, read the abstracts from the apper and and process them to create a [tidy](https://www.jstatsoft.org/article/view/v059i10) data structure without [stop words](https://en.wikipedia.org/wiki/Stop_words).

```{r}
tidy_abstracts <- papers %>%
  select(id, filename, abstract) %>%
  arrange(id)
  
  
papers_words <- tidy_abstracts %>%
    select(abstract) %>%
    unnest_tokens(word, abstract)
```



```{r calculate_stopword_stats, echo=FALSE}
total_words = nrow(papers_words)
#after_cleanup = nrow(no_stop_words)
```
