---
title: "R Notebook - exploratory analysis of survey papers for JMIR paper"
date: "`r format(Sys.Date())`"
output:
  html_document:
    df_print: paged
---

## Metadata

Required libraries and runtime environment description.

```{r load_libraries, echo=TRUE, message=FALSE, warning=FALSE}
library(here)
library(emidata)
library(tidyverse)
library(tidytext)
library(kableExtra)
library(stringr)
library(skimr)
library(ggalt)
library(scales)
#library(easyalluvial)
library(RColorBrewer)
library(gridExtra)
library(treemap)

library(forcats)

```


```{r session_info, echo=FALSE}
#devtools::session_info(include_base = TRUE)
```

This document is an EDA notebook to explore descriptive and informative figures of the datasets incldued in the *emidata* package.  

## Data 

We analyse three datasets: 

* *ipapers2018_psydata* (extracted data items related to psychology) has `` `r nrow(ipapers2018_psydata)` `` records and `` `r ncol(ipapers2018_psydata)` `` columns.
* *ipapers2018_csdata* (extracted data items related to tech/cs) has `` `r nrow(ipapers2018_csdata)` `` records and `` `r ncol(ipapers2018_csdata)` `` columns. 
* *ipapers2018* (list of analysed papers) has `` `r nrow(ipapers2018)` `` records and `` `r ncol(ipapers2018)` `` columns.

```{r data_source, echo=FALSE}
cs_data <- ipapers2018_csdata
psy_data <- ipapers2018_psydata
# cs_data %>% glimpse()
# cs_data %>% skimr::skim()
# psy_data %>% glimpse()
# psy_data %>% skimr::skim()

```


```{r all_data, echo=FALSE}

all_data <- psy_data %>%
    inner_join(cs_data, by="id")

# Drop "included" columns
all_data <- all_data %>% select(-id_csin, -id_psyin)

all_data <- all_data %>%
    inner_join(ipapers2018, by="id") %>%
    select(-filename, -title, -abstract, -journal, -author, -keywords)

# cast MD to factor
all_data$md <- factor(all_data$md, levels=names(sort(table(all_data$md), decreasing=T)))

#' Merge two factors levels into a new one "26-Various" 
all_data$md <- 
    all_data$md %>% 
    fct_collapse("26-Various" = c("23-Duo","24-Multiple"))

#' Sync changes of "md" to other two columns, "md_id"" and "md_desc""
all_data <- 
    all_data %>% 
        separate(md, c("md_id","md_desc"), "-", extra="merge", remove=FALSE)

all_data$md <- factor(all_data$md, levels=names(sort(table(all_data$md), decreasing=T)))

n_md <- nlevels(all_data$md)
n_papers = nrow(all_data)

#all_data %>% str()
```

The final number of papers to analyse is `` `r n_papers` ``.


```{r my_functions, echo=FALSE}


```



## Exploratory analysis of mental disorders (MDs)

Next exploratory tables and figures attempt to figure out what's going on. The initial assumption of the paper is that the field of mental disorder (*md*) drives the analysis. So we start exploring the related columns (variables), which are: 

```{r md_variables, echo=FALSE}
all_data %>%
    select(starts_with("md")) %>%
    names() 

```

### How many distinct MDs are there?

```{r md_variability, echo=FALSE}

category_levels <- c("YES","NO")
all_data <- 
    all_data %>%
    mutate(md_dsm5 = factor(if_else(md_id <= 22, "YES", "NO"), levels=category_levels))

n_yes_dsm5 <- 
    all_data %>%
        filter(md_dsm5 == "YES") %>%
        nrow()

n_no_dsm5 <- 
    all_data %>%
        filter(md_dsm5 == "NO") %>%
        nrow()

#all_data %>% str() 


```

There are `` `r n_md` `` distinct MDs (out of 25). About `r percent(n_yes_dsm5/n_papers)` (N=`r n_yes_dsm5`) are categorised according to Section II of  [DSM-5 manual](https://dsm.psychiatryonline.org/doi/book/10.1176/appi.books.9780890425596). About `r percent(n_no_dsm5/n_papers)` (N=`r n_no_dsm5`) are 23-Dual, 24-Multiple or 25-Suicidal behavior disorder/nonsuicidal self-injury. 


```{r plot_md_variability, echo=FALSE}
# plot variety of mental disorders

all_data %>%
  ggplot(mapping = aes(x = md, fill=md_dsm5)) +
    geom_bar() +
    coord_flip() +
    geom_text(stat = 'count', aes(label = ..count..), nudge_y = 0.5, size = 2) +
    labs(title="Distribution of MDs", subtitle = "Ranked by absolute count.") + 
    theme_bw()

```

Remarks:

* There appears to be three main groups of MDs: 1/ well-addressed, 2/ marginal, and 3/ ignored. In the group 1, we have for instance the last 4 rows of the above plot, which cover a good proportion of the papers. The second group refers to those MDs that have a reduce number of apps, say less than 4. They are for example the first rows of the above plot. The third group is the MDs that are not shown in the plot. 


```{r lollipop_md_variability, echo=FALSE}

md_percent <- 
    all_data %>%
      group_by(md, md_desc) %>%
      summarise(n = n()) %>%
      mutate(proportion = n/n_papers) %>%
      arrange(desc(n))

# head(md_percent)

md_percent %>%
    ggplot(aes(y=reorder(md_desc, proportion), x=proportion)) +
    geom_lollipop(point.colour = 'steelblue', point.size = 2,horizontal = TRUE) +
    scale_x_continuous(expand=c(0,0), labels=scales::percent_format(accuracy = 1), breaks=seq(0, 0.20, by=0.02), limits=c(0, 0.20)) +
    theme_minimal() +
    labs(title="Proportional distribution \nof metal disorders",
         subtitle=paste0("(N=",n_papers, ")"),
         x="Percentage",
         y="Mental disorders",
         caption="Source: authors") +
    theme(panel.grid.major.y=element_blank()) +
    theme(panel.grid.minor=element_blank()) +
    theme(axis.line.y=element_line(color="#2b2b2b", size=0.15)) +
    theme(axis.text.y=element_text(margin=margin(r=0, l=0))) +
    theme(plot.margin=unit(rep(20, 4), "pt")) +
    theme(plot.title=element_text(face="bold")) +
    theme(plot.subtitle=element_text(margin=margin(b=10)))

```


### [KEY FIGURE] Distribution of papers per Mental Health + Assessment


```{r plot_md_variability_assessment, echo=FALSE}
# plot variety of mental disorders per assessment 


md_data_kp <- 
    all_data %>%
    select(md, md_id, md_desc, val_ass)

md_data_kp <- 
    md_data_kp %>% 
        group_by(md_id, md_desc, val_ass) %>%  # first create counts for each group
        summarise(number_cases = n()) %>%
        # Create total counts and proportions per mental disorder
        group_by(md_desc) %>%
        mutate(total_cases = sum(number_cases),
               proportion = number_cases/total_cases) %>% 
        ungroup() %>%
        arrange(desc(total_cases), md_id)


# convert to factor to retain sorted order in plot.
md_data_kp$md_desc <- factor(md_data_kp$md_desc, levels=unique(md_data_kp$md_desc))  

        # Create total counts and proportions per assessment  
        # group_by(val_ass) %>%
        # summarise(number_cases_ass = n()) %>%
        # mutate(total_cases_ass = sum(number_cases_ass),
        #        proportion_ass = number_cases_ass/total_cases_ass) %>% 
        # ungroup()

kp_barchart <- 
    md_data_kp %>%
      ggplot(aes(x=md_desc, y=number_cases, label=number_cases)) + #, fill=val_ass, group= val_ass)) +
        geom_bar(stat="identity", aes(fill = val_ass), position = position_stack(reverse = T)) +
        geom_text(aes(label=number_cases), size=2, nudge_y = 0.2) +
        # geom_text(aes, (label=  color), , nudge_x= 0,  size = 2) +
        labs(title="Distribution of papers per mental disorder", 
             subtitle = paste0("(N=",n_papers, ")"),
             x="Mental disorders", 
             y="Number of cases", 
             caption="Source: authors") + 
        coord_flip() +
        guides(fill=guide_legend(title="Assessment")) +  # modify legend title
        scale_fill_brewer(palette = "Set2") +
        scale_y_continuous(expand=c(0,0), breaks=seq(0, 22, by=2), limits=c(0, 22)) +
        theme_minimal()  +
        # Legend: Top-Right Inside the Plot") 
        theme(legend.title = element_text(size=11), 
              legend.justification = c('right', 'top'),
              legend.position=c(0.95, 0.95),  
              #legend.background = element_blank(),
              legend.background = element_rect(color = "darkgray", size = 0.5, linetype ="solid"),
              legend.key = element_blank()) +
        # Change the line type and color of axis lines
        # theme(axis.line = element_line(colour = "darkgray", size = 1, linetype = "solid")) +
        # theme(panel.grid.minor=element_blank()) +
        # theme(panel.grid.major.y=element_blank())
        
        theme(panel.grid.major = element_blank()) + 
        theme(panel.grid.minor = element_blank()) +
        theme(panel.background = element_blank()) +
        theme(plot.margin=unit(rep(20, 4), "pt")) +
        theme(axis.line = element_line(colour = "darkgray", size = 0.5, linetype = "solid"))

kp_barchart
kp_file_name <- "fig_barchart.png"
ggsave(plot = kp_barchart, filename = kp_file_name, device = "png", path = here::here("figs"),
    scale = 1, width = 20, height = 12, units = "cm", dpi = "print") #300


# 
# kp_variability <- 
#     md_data_kp %>%
#       ggplot(mapping = aes(x = md_desc, fill=val_ass, group= val_ass)) +
#         geom_bar() +
#         geom_text(stat = 'count', aes(label = ..count..), nudge_y = 0.5, nudge_x= 0,  size = 2) +
#         labs(title="Distribution of papers per mental disorder", 
#              subtitle = paste0("(N=",n_papers, ")"),
#               x="Mental disorders", y="Number of cases", caption="Source: authors") + 
#         coord_flip() +
#         guides(fill=guide_legend(title="Assessment")) +  # modify legend title
#         scale_fill_brewer(palette = "Set1") +
#         theme_bw() +
#         # Legend: Top-Right Inside the Plot") 
#         theme(legend.title = element_text(size=11), 
#               legend.justification = c('right', 'top'),
#               legend.position=c(0.95, 0.95),  
#               #legend.background = element_blank(),
#               legend.background = element_rect(color = "gray", size = 0.5, linetype ="solid"),
#               legend.key = element_blank()) +
#         # Change the line type and color of axis lines
#         theme(axis.line = element_line(colour = "gray", size = 1, linetype = "solid"))
#     
# kp_variability
# kp_file_name <- "fig_dist.png"
# ggsave(plot = kp_variability, filename = kp_file_name, device = "png", path = here::here("figs"),
#     scale = 1, width = 20, height = 12, units = "cm", dpi = "print") #300

```


### Top3 MDs? 

```{r md_top5, echo=FALSE}
top3 <- levels(all_data$md)[1:3]

n_top3 <- 
    all_data %>%
        filter(md %in% top3) %>%
        nrow()

md_top3 <- 
    all_data %>%
      filter(md %in% top3) %>%
      group_by(md) %>%
      summarise(number_cases = n()) %>%
      mutate(proportion = round(number_cases/n_papers, 2)) %>%
      arrange(desc(number_cases))

md_top3
```

The *top3* MDs are categorised in the DSM-5, and they all cover about `r percent(n_top3/n_papers)` (N=`r n_top3`).

```{r lollipop_top3, echo=FALSE}

# md_top3 %>%
#     ggplot(aes(y=reorder(md, n_per), x=n_per)) +
#     geom_lollipop(point.colour = 'steelblue', point.size = 2,horizontal = TRUE) +
#     scale_x_continuous(expand=c(0,0), labels=percent, breaks=seq(0, 1, by=0.2), limits=c(0, 1)) +
#     theme_minimal() +
#     labs(x=NULL, y=NULL, 
#         title="TOP3 mental disorders",
#         subtitle="Ranked by relative %",
#         caption="Data from ...") + 
#     theme(panel.grid.major.y=element_blank()) +
#     theme(panel.grid.minor=element_blank()) +
#     theme(axis.line.y=element_line(color="#2b2b2b", size=0.15)) +
#     theme(axis.text.y=element_text(margin=margin(r=0, l=0))) +
#     theme(plot.margin=unit(rep(30, 4), "pt")) +
#     theme(plot.title=element_text(face="bold")) +
#     theme(plot.subtitle=element_text(margin=margin(b=10))) +
#     theme(plot.caption=element_text(size=8, margin=margin(t=10)))


```

### Variability of MDs over time?

_Note: The period 2013-2017 covers full years. 2018 only covers the first two months (Bibliographic searches were conducted at the beginning of March 2018)._ 

```{r md_years, echo=FALSE}

all_data %>%
  ggplot(mapping = aes(x = md, fill=md_dsm5)) +
    geom_bar() +
        coord_flip() +
    geom_text(stat = 'count', aes(label = ..count..), nudge_y = 0.5, size = 2) +
    theme_bw() + 
    labs(title="Distribution of MDs by year", subtitle = "Absolute count. Colored by belonging to DSM-5") + 
    facet_wrap(~ year)

```

Remarks:

* There is no clear temporal trend. Only that the last years attract more papers. 
* In terms of variability, we can say that the range of MD addressed in papers is expanding in recent years
* We can say that the range oftop3`) remain significant over all years.


```{r md_years_area, echo=FALSE}

all_data %>% 
    group_by(year) %>%  # first create counts for each group
    summarise(number_cases = n()) %>% 
    ggplot(aes(x=year, y=number_cases )) +
    geom_area(colour="cornflowerblue", fill = "cornflowerblue", 
              alpha=0.5, # Make the fill see through 50%)
              size=0.5) + # Make the size of the borders smaller
    geom_text(aes(label = number_cases), color= "blue", nudge_y = -1, size = 3) +
    geom_vline(aes(xintercept = 2017), linetype = 'dashed', size = 0.5)


```


Remarks:

* There is a sharp peak in 2016-2017 compared to 2013-2015. Speculating a bit, it is plausible to say that the number of documents eligible for the years between 2008 and 2012 would have represented a small part of the total number of eligible documents, especially when compared with the last 5 years (2013-2018).
* The 2015-2016 period accounts for (`r percent(60/n_papers)`), while 2013-2015 accounts for (`r percent(32/n_papers)`).
* Only two months of 2018 (`r percent(12/n_papers)`) almost reach the amount of documents in 2012 and 2013 together (`r percent(15/n_papers)`).


### [KEY FIGURE] Variability Of MDs and top3 over time


```{r}

totalcount_byyear <- 
    all_data %>% 
    group_by(year) %>%  # first create counts for each group
    summarise(number_cases = n()) %>%
    mutate(md_desc = c("All"))


md_top3_byyear <- 
    all_data %>%
      filter(md %in% top3) %>%
      group_by(md_desc, year) %>%
      summarise(number_cases = n()) %>%
      bind_rows(totalcount_byyear) %>%
      ungroup() %>%
      mutate(md_desc = factor(md_desc)) %>%
      arrange(desc(number_cases))

# https://www.r-graph-gallery.com/portfolio/ggplot2-package/
# https://ggplot2.tidyverse.org/reference/position_stack.html


md_top3_byyear$md_desc <- fct_relevel(md_top3_byyear$md_desc, c("All", "Depressive disorders", "Various", "Anxiety disorders"))

    
kp_linechart <-
md_top3_byyear %>%
    ggplot(aes(x=year, y=number_cases, group=md_desc)) +
    geom_line(aes(color=md_desc), size=1, alpha=.4) +
    geom_point(aes(color=md_desc), size=6) +
    labs(title="Distribution of papers per year", 
         subtitle = "Total and top3 mental disorders",
         x="Year", 
         y="Number of cases", 
         caption="Source: authors") + 
    scale_color_brewer(palette="Set2", breaks=levels(md_top3_byyear$md_desc)) +
    geom_text(aes(label = number_cases), color= "white", size=3) +
    geom_vline(aes(xintercept = 2017), color="darkgray", linetype = "dashed", size = 0.5) +
    annotate("rect", xmin = 2017, xmax = 2018, ymin = -Inf, ymax = +Inf, fill = "lightgray", alpha = 0.2) +
    theme_minimal() +
    theme(legend.title = element_blank()) +
    # Legend: Top-Right Inside the Plot") 
    theme(legend.justification = c('left', 'top'),
          legend.position=c(0.05, 0.95),  
          #legend.background = element_blank(),
          legend.background = element_rect(color = "darkgray", size = 0.5, linetype ="solid"),
          legend.key = element_blank()) +
    theme(panel.grid.major = element_blank()) + 
    theme(panel.grid.minor = element_blank()) +
    theme(panel.background = element_blank()) +
    theme(plot.margin=unit(rep(20, 4), "pt")) +
    # Change the line type and color of axis lines
    theme(axis.line = element_line(colour = "darkgray", size = 0.5, linetype = "solid"))

kp_linechart
kp_file_name <- "fig_linechart.png"
ggsave(plot = kp_linechart, filename = kp_file_name, device = "png", path = here::here("figs"),
    scale = 1, width = 20, height = 12, units = "cm", dpi = "print") #300

# library(ggridges)
# md_top3_byyear %>%
# ggplot(aes(x =year, y=md, fill=md)) +
#   geom_density_ridges() +
#   theme_ridges() + 
#   theme(legend.position = "none")
# 
# 
# all_data %>% 
#     group_by(year) %>%  # first create counts for each group
#     summarise(number_cases = n()) %>% 
#     ggplot(aes(x=year, y=number_cases)) +
#     geom_area(colour="cornflowerblue", fill = "cornflowerblue", 
#               alpha=0.5, # Make the fill see through 50%)
#               size=0.5) + # Make the size of the borders smaller
#     geom_text(aes(label = number_cases), color= "blue", nudge_y = -1, size = 3) +
#     geom_vline(aes(xintercept = 2017), linetype = 'dashed', size = 0.5)


```





```{r md_years_alluvial, echo=FALSE}

#' TODO ONGOING
md_by_year <- 
    all_data %>% 
    group_by(md_id, md_desc, year) %>%  # first create counts for each group
    summarise(number_cases = n()) %>% 
    group_by(year) %>%
    mutate(total_cases = sum(number_cases),
           proportion = number_cases/total_cases) %>% # Create total counts 
    ungroup() %>%
    as_tibble()

    
# md_by_year2 <- 
#     all_data %>% 
#     group_by(md_id, md_desc, year)  %>%    
#     expand(year)
# 
#     summarise(number_cases = n()) %>% 
#     expand(md_id, year, number_cases)
#     summarise(number_cases = n()) %>% 
#     group_by(year) %>%
#     mutate(total_cases = sum(number_cases),
#            proportion = number_cases/total_cases) %>% # Create total counts 
#       .[complete.cases(.), ]
#     ungroup() %>%
#     as_tibble()
    
    
# md_by_year %>%  str()


# source: https://www.r-bloggers.com/how-to-expand-color-palette-with-ggplot-and-rcolorbrewer/
n_colors <- length(unique(md_by_year$md_id))
get_palette <- colorRampPalette(brewer.pal(9, "Set1"))


# https://www.rdocumentation.org/packages/easyalluvial/versions/0.1.8/topics/alluvial_long
# alluvial_long(md_by_year, 
#               key = year, 
#               value = proportion, 
#               id = md_id, 
#               bins = n_colors,
#               NA_label = "NA",
#               bin_labels = as.character(unique(md_by_year$md_id)),
#               fill_by = 'all_flows',
#               col_vector_flow = get_palette(n_colors),
#               col_vector_value = get_palette(n_colors)
# )
      

```



### Comorbidity in cases 23-Dual and 24-multiple? 

Reminder: About `r percent(n_no_dsm5/n_papers)` (N=`r n_no_dsm5`) are 23-Dual, 24-Multiple or 25-Suicidal Behavior Disorder/Nonsuicidal Self-Injury. We look now at 23-Dual and 24-Multiple MDs, and check the field *md_mul* that lists the mutliple MDs.

```{r commorbidity, echo=FALSE}

# TODO http://stulp.gmw.rug.nl/ggplotworkshop/twodiscretevariables.html

md_23or24 <- 
    all_data %>% 
    filter(md_id==23 | md_id==24) %>% 
    separate_rows(sep = ";", md_mul)

md_23or24$md_mul <- str_trim(md_23or24$md_mul)

md_23or24 <- 
    md_23or24 %>% 
      group_by(md_mul, md_id) %>%  # first create counts for each group
      summarise(number_cases = n()) %>%
      group_by(md_mul) %>%
      mutate(total_cases = sum(number_cases),
             proportion = number_cases/total_cases) # Create total counts 

#head(md_23or24)
```

A way to visualize the two discrete variables is by using a bar plot (counts) and a stacked bar plot (proportions).

```{r plot_commorbidity, echo=FALSE}


#plot_left <- 
md_23or24 %>%
  ggplot(aes(x=md_mul, y=number_cases, fill=factor(md_id))) + 
  geom_bar(stat="identity") +
  coord_flip() + 
  labs(title="Commorbidity. Absolute count") +
  theme_minimal()

#plot_right <- 
md_23or24 %>%
    ggplot(aes(x=md_mul, y=proportion, fill=factor(md_id))) + 
    geom_bar(stat="identity", position="stack") +
    geom_text(aes(x=md_mul, y=0.05, label=total_cases), size=3, colour="white") +
    scale_y_continuous(labels = scales::percent_format()) +
    coord_flip() +
    labs(title="Commorbidity. Proportional stacked bar") +
    theme_minimal()


#gridExtra::grid.arrange(plot_left, plot_right, nrow = 1)
```

Same as the above stacked bar plot but using a bubble plot.

```{r bubbleplot_commorbidity, echo=FALSE }
# Source: http://stulp.gmw.rug.nl/ggplotworkshop/twodiscretevariables.html#bubbleplot

md_23or24 %>%
    ggplot(aes(x=md_mul, y=factor(md_id))) +
    geom_count(aes(size=..prop..), colour="lightgrey") +
    geom_point(aes(size=proportion), colour="cornflowerblue") + 
    scale_size(range = c(0,10), breaks=seq(0,1,by=0.2)) +
    #scale_size(range = c(0.4,1.0), breaks=seq(0.4,1.0,by=0.1)) +
    #geom_point(aes(size=proportion)) + 
    coord_flip() +
    labs(title="Commorbidity. Proportional bubble plot") +
    theme_minimal()


```


### What subtypes of illnesses are mentioned (in the papers) per each category of mental disorder in DSM-5?

We look at MDs which are categorised according to the DSM-5 (id <= 22 or id = 25), and check the field *md_sub*.

```{r subtypes_dotplot, echo=FALSE}
#' Source: http://stulp.gmw.rug.nl/ggplotworkshop/twodiscretevariables.html
md_subtypes <- 
    all_data %>% 
    filter(md_id!=23 & md_id!=24) %>%
    drop_na(md_sub) %>%
    arrange(desc(md_id))

n_colors <- nlevels(factor(md_subtypes$md_id))
get_palette <- colorRampPalette(brewer.pal(8, "Set2"))

#' Source: https://ggplot2.tidyverse.org/reference/geom_dotplot.html
#' source: http://www.sthda.com/english/wiki/ggplot2-dot-plot-quick-start-guide-r-software-and-data-visualization
md_subtypes %>%
    ggplot(aes(x=factor(md_sub), fill=factor(md_id)), group=factor(md_id), colour=get_palette(n_colors)) + 
    geom_dotplot(method="dotdensity", binwidth=1, stackdir = "center", stackratio=1.2) + 
    #geom_dotplot(method="histodot", binwidth=1, stackdir = "center") + 
    scale_y_continuous(name=NULL, breaks=NULL) +
    coord_flip() +
    labs(title="Subtypes of MDs as dotplot.", subtitle ="Absolute count.") +
    theme(legend.position="bottom") +
    theme_minimal()

#' TODO: Reorder the factor (md_mul) to group subtypes per main MD. For example, all depression-related subtypes must be shown together 


```



```{r subtypes_alluvial, echo=FALSE}

#' TODO ONGOING

# md_subtypes %>%
#     group_by(md_id, md_desc, md_sub)  %>%  # first create counts for each group
#     summarise(number_cases = n())


#separate_rows(sep = ";", md_mul)

#' ggalluvial, source: https://cran.r-project.org/web/packages/ggalluvial/vignettes/ggalluvial.html
#' ggalluvial, source: http://corybrunson.github.io/ggalluvial/index.html
#' easyalluvial, source: https://github.com/erblast/easyalluvial/blob/master/README.md
library(ggalluvial)

# TODO: Error: Too many colors
# md_subtypes %>%
#     group_by(md_id, md_sub)  %>%  # first create counts for each group
#     summarise(number_cases = n()) %>%
#     ggplot(aes(y = number_cases, axis1=md_id, axis2=md_sub)) +
#     geom_alluvium(aes(fill=md_sub), width = 1/12) +
#     geom_stratum(width = 1/12, fill = "black", color = "grey") +
#     geom_label(stat = "stratum", label.strata = TRUE) +
#     #scale_x_discrete (breaks = 1:2, labels = c("MD", "Subtype")) +
#     scale_x_discrete(limits = c("MDs", "Subtypes"), expand = c(.05, .05)) +
#     scale_fill_brewer(type = "qual", palette = "Set1") +  
#     theme(legend.position = "bottom") +
#     labs(title="Mental disorders and subtypes. Alluvial plot") +
#     theme_minimal()


# md_subtypes %>%
#     group_by(md_id, md_sub)  %>%  # first create counts for each group
#     summarise(number_cases = n()) %>%
#     ggplot(aes(y = number_cases, axis1=md_id, axis2=md_sub)) +
#     stat_stratum(geom = "errorbar") +
#   geom_line(stat = "alluvium") +
#   stat_alluvium(geom = "pointrange") +
#   geom_text(stat = "stratum", label.strata = TRUE) +
#   scale_x_discrete(limits = c("MDs", "Subtypes"), expand = c(.05, .05))


#' circlize, source: http://jokergoo.github.io/circlize/example/bi_directional.html
    

```


### Mental disorders and phsycological framework

_Which is the total coverage of CBT?_ _And the coverage of the rest of phsycological framework?_

_Which DMs are related to third wave theraphy and /or positive Psychotherapy?_


## Exploratory analysis of mental disorders and apps

### Number of apps related to each MD 

Let's start simple: _How many apps are related to the MDs and subtypes?_ 

```{r md_apps, echo=FALSE}

# # TODO: Ongoing
n_apps <- 
    all_data %>% 
    filter(md_id!=23 & md_id!=24) %>% 
    group_by(md_id, md_desc, md_sub) %>%
    #drop_na(md_sub)%>%
    summarise(number_apps = n()) 

n_apps %>%
  ggplot(aes(x=md_sub, y=number_apps, fill=factor(md_id))) + 
  geom_bar(stat="identity") +
  coord_flip() + 
  labs(title="Apps per subtopic coloured by MD",
       subtitle = "Absolute count") +
  theme(legend.position = "top") +
  theme_minimal()


```

Note that in the above bar chart, there is a significant proportion of app whose subtopic is not defined (NA). Are therefore these apps too much generic?  


We use a [treemap](https://cran.r-project.org/package=treemap) diagram to represent hierarchical data in the form of nested rectangles, the area of each corresponding to its numerical value. i.e. the count of apps per subtype and main MD

```{r md_apps_treemap, echo=FALSE}

n_apps %>%
    treemap(
        index=c("md_desc","md_sub"),  #A list of your categorical variables
        vSize = "number_apps",  #This is your quantitative variable
        type="index", #Type sets the organization and color scheme of your treemap
        palette = "Greens",  #Select your color palette from the RColorBrewer presets or make your own.
        title="Number of apps per subtype and main category of MDs", 
        fontsize.title = 14 #Change the font size of the title
    )

```

### Sensory capabilities related to each MD 

```{r md_apps_table, echo=FALSE}
cols = c("id", "md", "md_id", "md_desc", "md_sub", "md_dsm5",
         "sens_acc", "sens_gyr", "sens_gps", "sens_mic", 
         "os_ios", "os_and", "app_name", 
         "type", "year")

sens_apps <- 
    all_data %>% 
    filter(md_id!=23 & md_id!=24) %>%
    select(cols) %>%
    arrange(md_desc, md_sub)
    # group_by(md_desc, md_sub) %>%
    # summarise(number_apps = n()) 


#' source: https://cran.r-project.org/web/packages/kableExtra/vignettes/awesome_table_in_html.html
sens_apps %>%
    # mutate(sens_acc = cell_spec(sens_acc, color = ifelse(sens_acc=="YES", "blue", "red"))) %>%
    select(`DSM-5 Mental Disorder` = md_desc,
           `MD Subtype` = md_sub,
           `Accelerometer` = sens_acc,
           `Ggyroscope` = sens_gyr,
           `GPS` = sens_gps,
           `Microphone` = sens_mic,
           `App Name` = app_name) %>%
    kable(format = "html", escape = FALSE) %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))


```

Now, we filter the records that have any value from the "sens_" fields to true. Heatmeap?

```{r md_apps_sensors, echo=FALSE}

heatmap_data <- 
    sens_apps %>%
    filter(sens_acc == "YES" | sens_gyr =="YES" | sens_gps == "YES" | sens_mic == "YES")

heatmap_data %>%
    select(`DSM-5 Mental Disorder` = md_desc,
           `MD Subtype` = md_sub,
           `Accelerometer` = sens_acc,
           `Ggyroscope` = sens_gyr,
           `GPS` = sens_gps,
           `Microphone` = sens_mic,
           `App Name` = app_name) %>%
    kable(format = "html", caption = "Apps", escape = FALSE) %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))



```


```{r}


```




### BELOW THIS LINE IS NOT VALID

```{r plot_dumbbell, echo=FALSE}


# df <- data.frame(trt=LETTERS[1:5], l=c(20, 40, 10, 30, 50), r=c(70, 50, 30, 60, 80))
# 
# ggplot(df, aes(y=trt, x=l, xend=r)) + 
#   geom_dumbbell(size=3, color="#e3e2e1", 
#                 colour_x = "#5b8124", colour_xend = "#bad744",
#                 dot_guide=TRUE, dot_guide_size=0.25) +
#   labs(x=NULL, y=NULL, title="ggplot2 geom_dumbbell with dot guide") +
#   theme_minimal() +
#   theme(panel.grid.major.x=element_line(size=0.05)) +
#   theme(panel.grid.major.y=element_blank())

```




```{r echo=FALSE}
# md_data %>%
# ggplot(mapping = aes(x = md, y = n, fill = md_dsm5)) +
#     geom_bar(stat="identity") +
#     coord_flip() +
#     geom_text(aes(label = n), nudge_y = 0.5, size = 2) +
#     theme_bw()
# 
# 
# geom_text(stat = 'count' ,aes(label = ..count..),
# nudge_y = 1.5)
# 
# 
# md_data %>%
#   group_by(md) %>%
#   summarise(n = n()) %>%
#   arrange(desc(n))  %>%
#   ggplot(mapping = aes(x = reorder(md, y = n)) +
#     geom_bar(stat="identity", fill="orange") +
#     coord_flip() +
#     geom_text(aes(label = n), nudge_y = 0.5, size = 2) +
#     theme_bw()
```




