---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---

## Metadata

Required libraries and runtime environment description.

```{r load_libraries, echo=TRUE, message=FALSE, warning=FALSE}
library(emidata)
library(tidyverse)
library(tidytext)
library(kableExtra)
library(stringr)
library(wordcloud)
library(skimr)

```


```{r session_info, echo=FALSE}
devtools::session_info(include_base = TRUE)
```

This document is an EDA notebook to explore descriptive and informative figures of the dataset *ipapers2018* in the *emidata* package. Type `?ipapers2018` for information. 

## Data 

The data for the analysis is in the *ipapers2018* dataset that has `` `r nrow(ipapers2018)` `` references.

```{r data_source, echo=FALSE}
papers <- ipapers2018
papers %>% glimpse()
papers %>% skimr::skim()
```

As part of the text analysis of papers, including wordcloud and terms frequency analysis, read the full list of abstracts from the `papers` and process them to create a [tidy](https://www.jstatsoft.org/article/view/v059i10) data structure without [stop words](https://en.wikipedia.org/wiki/Stop_words). Reference book to text mining in tidy format: [Text Mining with R](https://www.tidytextmining.com/)

```{r stopwords_abstract, echo=FALSE}
tidy_abstracts <- papers %>%
  select(id, abstract) %>%
  arrange(id)
  
papers_words <- tidy_abstracts %>%
    select(id, abstract) %>%
    unnest_tokens(word, abstract)

my_stop_words <- tibble(
  word = c(
    "et",
    "al",
    "fig",
    "e.g",
    "i.e",
    "http",
    "ing",
    "pp",
    "figure",
    "based",
    "â",
    "background", # used to structure an abstract
    "objective",
    "methods",
    "results",
    "conclusions"
    ),
  lexicon = "jmir")


all_stop_words <- stop_words %>%
  bind_rows(my_stop_words)

# Get rid of numeric values (as words) from abstracts
suppressWarnings({
  no_numbers <- papers_words %>%
    filter(is.na(as.numeric(word)))
})

# Get list of words from abstracts without stopwords 
no_stop_words <- no_numbers %>%
  anti_join(all_stop_words, by = "word") 

```

```{r stopwords_abstract_EDA, echo=FALSE}

# papers_words %>%
#     count(word, sort = TRUE) %>%
#     filter(n > 200) %>%
#     mutate(word = reorder(word, n)) %>%
#     ggplot(aes(word, n)) +
#     geom_col() +
#     xlab(NULL) +
#     coord_flip()


```


```{r calculate_stopword_stats, echo=FALSE}
total_words = nrow(papers_words)
after_cleanup = nrow(no_stop_words)
```

About `r round(after_cleanup/total_words * 100)` % (`r after_cleanup`) of the total words (`r total_words`) are considered stop words.

_How many non-stop words does each abstract have?_

```{r non_stopwords_abstract, echo=FALSE}

non_stop_words_per_abstract <- no_stop_words %>%
  group_by(id) %>%
  summarise(num_words = n()) %>%
  left_join(papers, by=c("id")) %>%
  select(id, filename, num_words, year) %>%
  arrange(desc(num_words))

non_stop_words_per_abstract$id <- factor(non_stop_words_per_abstract$id, 
                                               levels = non_stop_words_per_abstract$id[order(non_stop_words_per_abstract$num_words)])
```



```{r echo=FALSE}

ggplot(slice(non_stop_words_per_abstract, 1:40), aes(id, num_words, fill=year)) + 
  geom_col(show.legend = FALSE) +
  labs(x = NULL, y = "# words", title="Top40 abstracts by # words, by year") +
  facet_wrap(~year, ncol = 2, scales = "free")+
  coord_flip() 


kable(slice(non_stop_words_per_abstract, 1:20),
  caption = "Top20 abstracts ordered by # words after deleting stopwords.", 
  format = "html", booktabs = TRUE)

```

## Search terms in the abstract

### Psychological terms

The detection matches full words using regex option `\b`.

- mental (and also e-mental)
- psycholog (`psycholog.*`, i.e. psychology, psychological)
- psychiatric
- emotional
- health (and also e-health, u-health)
- treatment(s) (and also pretreatment, post-treatment)
- disorder(s) 
- intervention(s) 
- therapy(ies)
- distress,
- affection
- depressi (`depressi.*`, i.e. depression, depressive)
- anxiety,
- ecological momentary intervention

```{r psy_search_terms_per_abstract, echo=FALSE}
tidy_abstracts_lower <- stringr::str_to_lower(tidy_abstracts$abstract)
psy_terms_count <- tibble(
  id = tidy_abstracts$id,
  mental = stringr::str_count(tidy_abstracts_lower, "\\bmental\\b"),
  `psycholog..` = str_count(tidy_abstracts_lower, "\\bpsycholog.*\\b"),
  psychiatric = stringr::str_count(tidy_abstracts_lower, "\\bpsychiatric\\b"),
  emotional = stringr::str_count(tidy_abstracts_lower, "\\bemotional\\b"),
  health = stringr::str_count(tidy_abstracts_lower, "\\bhealth\\b"),
  `treatment(s)` = stringr::str_count(tidy_abstracts_lower, "\\btreatments?\\b|\\bpretreatment?\\b"),
  `disorder(s)` = stringr::str_count(tidy_abstracts_lower, "\\bdisorder?\\b"),
  `intervention(s)` = stringr::str_count(tidy_abstracts_lower, "\\bintervention?\\b"),
  `therapy/ies` = stringr::str_count(tidy_abstracts_lower, "\\btherap(y|ies)\\b"),
  distress = stringr::str_count(tidy_abstracts_lower, "\\bdistress\\b"),
  affection = stringr::str_count(tidy_abstracts_lower, "\\baffection\\b"),
  `depressi..` = str_count(tidy_abstracts_lower, "\\bdepressi.*\\b"),
  anxiety = stringr::str_count(tidy_abstracts_lower, "\\banxiety\\b"))
  # emi = stringr::str_count(tidy_abstracts_lower, "\\becological momentary intervention\\b)"))
  # TODO; I cannot search by several words separated by blanck spaces (EMI case)

# sum a bunch of columns row-wise
# https://stackoverflow.com/a/32827260/261210
sumColsInARow <- function(df, list_of_cols, new_col) {
  df %>% 
    mutate_(.dots = ~Reduce(`+`, .[list_of_cols])) %>% 
    setNames(c(names(df), new_col))
}

# Sum all occurences of psy search terms row-wise (i.e. per abstract) and put result in a new column "all"
psy_terms_count_sum <- sumColsInARow(
  psy_terms_count, names(psy_terms_count)[names(psy_terms_count) != "id"], "psy_all") %>%
  arrange(desc(psy_all))

# Compute totals per column, i.e per each psy search term and "all"
psy_terms_count_sum_total <- psy_terms_count_sum %>% 
  summarise_if(is.numeric, funs(sum)) %>%
  add_column(id = "Total", .before = 0)
  
psy_terms_count_sum <- rbind(psy_terms_count_sum, psy_terms_count_sum_total)
```

_How often do psychological related search terms appear in each abstract?_

```{r  psy_search_terms_table, echo=FALSE}

# for testing
# kable(psy_terms_count_sum)
kable(psy_terms_count_sum %>% top_n(20),
      caption = paste0("Psychological-related search terms in the corpus,",
                       " ordered by sum of matches per abstract (top20)"),
      format = "html", booktabs = TRUE) %>%
  kableExtra::landscape()
```

### Technical terms

The detection matches full words using regex option `\b`.

- cell (and cell-phone, cellphone)
- mobile
- smart (and smartphone)
- portable
- phone(s) 
- device(s)
- app(s)
- applicat (`applicat.*`, i.e. application)
- emotional
- mhealth
- uhealth
- ehealth
- emental
- android
- iphone

```{r cs_search_terms_per_abstract, echo=FALSE}

cs_terms_count <- tibble(
  id = tidy_abstracts$id,
  cell = stringr::str_count(tidy_abstracts_lower, "\\bcell\\b"),
  mobile = stringr::str_count(tidy_abstracts_lower, "\\bpmobile\\b"),
  smart = stringr::str_count(tidy_abstracts_lower, "\\bsmart\\b"),
  portable = stringr::str_count(tidy_abstracts_lower, "\\bportable\\b"),
  `phone(s)` = stringr::str_count(tidy_abstracts_lower, "\\bphone?\\b"),
  `device(s)` = stringr::str_count(tidy_abstracts_lower, "\\bdevice?\\b"),
  `app(s)` = stringr::str_count(tidy_abstracts_lower, "\\bapp?\\b"),
  `applicat..` = str_count(tidy_abstracts_lower, "\\bapplicat.*\\b"),
  mhealth = stringr::str_count(tidy_abstracts_lower, "\\bmhealth\\b"),
  uhealth = stringr::str_count(tidy_abstracts_lower, "\\buhealth\\b"),
  ehealth = stringr::str_count(tidy_abstracts_lower, "\\behealth\\b"),
  emental = stringr::str_count(tidy_abstracts_lower, "\\bemental\\b"),
  android = stringr::str_count(tidy_abstracts_lower, "\\bandroid\\b"),
  iphone = stringr::str_count(tidy_abstracts_lower, "\\biphone\\b"))
  

# Sum all occurences of cs search terms row-wise (i.e. per abstract) and put result in a new column "all"
cs_terms_count_sum <- sumColsInARow(
  cs_terms_count, names(cs_terms_count)[names(cs_terms_count) != "id"], "cs_all") %>%
  arrange(desc(cs_all))

# Compute totals per column, i.e per each psy search term and "all"
cs_terms_count_sum_total <- cs_terms_count_sum %>% 
  summarise_if(is.numeric, funs(sum)) %>%
  add_column(id = "Total", .before = 0)
  
cs_terms_count_sum <- rbind(cs_terms_count_sum, cs_terms_count_sum_total)
```


_How often do Computer science related search terms appear in each abstract?_

```{r  cs_search_terms_table, echo=FALSE}

# for testing
#kable(cs_terms_count_sum)
kable(cs_terms_count_sum  %>% top_n(20),
      caption = paste0("Computer Sciece-related search terms in the corpus,",
                       " ordered by sum of matches per abstract (top20)"),
      format = "html", booktabs = TRUE) %>%
  kableExtra::landscape()
```


### Combined psycological and technical terms

```{r joint_search_terms, echo=FALSE}

joint <- psy_terms_count_sum %>%
  left_join(cs_terms_count_sum, by=c("id")) %>%
  select(id, psy_all, cs_all) %>%
  arrange(desc(psy_all)) %>%
  slice(-1)  # get rid of Total row


ggplot(joint, aes(x = cs_all, y = psy_all, color = cs_all - psy_all)) +
  geom_abline(color = "gray40", lty = 3) +
  geom_jitter(alpha = 0.1, size = 2.5, width = 0.3, height = 0.3) +
  geom_text(aes(label = id), check_overlap = TRUE, vjust = 1.5) +
  #scale_color_gradient(limits = c(0, 0.001), low = "darkslategray4", high = "gray75") +
  #facet_wrap(~author, ncol = 2) +
  #theme(legend.position="none") +
  labs(y = "# of psy search terms", x = "# of CS search terms", title ="Abstracts according total number of search terms")
```

Paper 101 (dark blue) ranks first with 23 appearances of search terms related to psychology in the abstract. On the other end, paper 183 (light blue) ranks first with 14 appearances of search terms related to computer science in the abstract. Looking at the plot, papers with psychology terms outnumber papers with computer scince terms. Dark blue numbers dominate 


## Frequency analysis of top words (most frequent) in the abstracts


### Figure: Word cloud of asbtracts (A), psyschology top words, and technical top words


```{r top_words, echo=FALSE}

countPapersUsingWord <- function(the_word) {
  sapply(the_word, function(w) {
    no_stop_words %>%
      filter(word == w) %>%
      group_by(id) %>%
      count %>%
      nrow
  })
}

# top25 words
no_top_words <- 25
top_words <- no_stop_words %>%
  group_by(word) %>%
  tally %>%
  arrange(desc(n)) %>%
  head(no_top_words) %>%
  mutate(`# abstracts` = countPapersUsingWord(word)) %>%
  add_column(place = c(1:nrow(.)), .before = 0)

```

_Word cloud of `r no_top_words` top words in abstracts_ 

```{r Fig_Word_cloud,dpi=600,fig.width=8,fig.asp=0.85, echo=FALSE}
set.seed(1)
if (max(top_words$n) < 100) {
  minimum_occurence <- round(mean(top_words$n))
} else {
  minimum_occurence <-  min(top_words$n) # Or arbritary number like 100 
}

cloud_words <- no_stop_words %>%
  group_by(word) %>%
  tally %>%
  filter(n >= minimum_occurence) %>% 
  arrange(desc(n))

if (nrow(cloud_words) > 0) {  
  plot.new()
  wordcloud(cloud_words$word, cloud_words$n,
            max.words = Inf,
            random.order = FALSE,
            fixed.asp = FALSE,
            rot.per = 0,
            #color = brewer.pal(8,"Dark2"))
            color = brewer.pal(9,"BuGn"))
} else {
  warning("No input data for wordcloud.")
}



```


This word cloud is based on `r length(unique(cloud_words$word))` unique words occuring each at least `r minimum_occurence` times, all in all occuring `r sum(cloud_words$n)` times which is roughly `r round(sum(cloud_words$n)/ nrow(no_stop_words) * 100)` % of the all non-stop words.


```{r  top_words_table, echo=FALSE}
# for testing
# kable(top_words)
kable(top_words,
      caption = paste0("Occurrences of top",no_top_words," words in the corpus"),
      format = "html", booktabs = TRUE)

```

```{r next_steps}
#TODO: How do top words and search terms correlate?
# Do it manually or automated. Which of the top words are also search terms? Are search terms in the top of the list? Are there standing top words that were nt search terms?
#TODO: Visualise table of occurrances of top words
#TODO: How do the top words correlated with the top keywords in the corpus?
#TODO: How do the top words correlated with the top keywords in each abstract?

```
 

