---
title: 'Analysis and visualisations for "JMIR paper title here"'
author: "Carlos Granell et al."
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    df_print: paged
    toc: yes
  pdf_document:
    keep_tex: yes
    #latex_engine: xelatex
    toc: yes
urlcolor: blue    
---

## License

This document is licensed under a [Creative Commons Attribution 4.0 International License](https://creativecommons.org/licenses/by/4.0/).


## Metadata

Required libraries and runtime environment description.

```{r load_libraries, echo=FALSE, message=FALSE, warning=FALSE}
library(here)
library(emidata)
library(tidyverse)
library(tidytext)
library(kableExtra)
library(stringr)
library(skimr)
# library(ggalt)
library(scales)
library(RColorBrewer)
library(gridExtra)
library(treemap)
library(forcats)
library(purrr)
library(hrbrthemes)  # TODO: see https://stackoverflow.com/questions/14733732/cant-change-fonts-in-ggplot-geom-text to solve font does not find

```


```{r session_info, echo=FALSE}
devtools::session_info(include_base = TRUE)
```

This document is versioned in a public [git](https://git-scm.com/) repo: [https://github.com/cgranell/emi-mhealth](https://github.com/cgranell/emi-mhealth).

\newpage

This R notebook contains the code to produce the final figures and tables of the paper. 

## Data 

Input datasets are the processed datasets within the *emidata* data package. The package code is available in a public [git](https://git-scm.com/) repo: [https://github.com/cgranell/emidata](https://github.com/cgranell/emidata). We analyse the follwing three datasets of the *emidata* package: 

* *ipapers2018_psydata* (extracted data items related to psychology) has `` `r nrow(ipapers2018_psydata)` `` records and `` `r ncol(ipapers2018_psydata)` `` columns.
* *ipapers2018_csdata* (extracted data items related to tech/cs) has `` `r nrow(ipapers2018_csdata)` `` records and `` `r ncol(ipapers2018_csdata)` `` columns. 
* *ipapers2018* (list of analysed papers) has `` `r nrow(ipapers2018)` `` records and `` `r ncol(ipapers2018)` `` columns.


```{r all_data, echo=FALSE}

cs_data <- ipapers2018_csdata
psy_data <- ipapers2018_psydata

all_data <- psy_data %>%
    inner_join(cs_data, by="id")

# Drop "included" columns
all_data <- all_data %>% select(-id_csin, -id_psyin)

all_data <- all_data %>%
    inner_join(ipapers2018, by="id") %>%
    select(-filename, -title, -abstract, -journal, -author, -keywords)

# cast MD to factor
all_data$md <- factor(all_data$md, levels=names(sort(table(all_data$md), decreasing=T)))

#' Merge two factors levels into a new one "26-Various" 
all_data$md <- 
    all_data$md %>% 
    fct_collapse("26-Various" = c("23-Duo","24-Multiple"))

#' Sync changes of "md" to other two columns, "md_id"" and "md_desc""
all_data <- 
    all_data %>% 
        separate(md, c("md_id","md_desc"), "-", extra="merge", remove=FALSE)

all_data$md <- factor(all_data$md, levels=names(sort(table(all_data$md), decreasing=T)))

n_md <- nlevels(all_data$md)
n_papers = nrow(all_data)

category_levels <- c("YES","NO")
all_data <- 
    all_data %>%
    mutate(md_dsm5 = factor(if_else(md_id <= 22, "YES", "NO"), levels=category_levels))

n_yes_dsm5 <- 
    all_data %>%
        filter(md_dsm5 == "YES") %>%
        nrow()

n_no_dsm5 <- 
    all_data %>%
        filter(md_dsm5 == "NO") %>%
        nrow()

```

The final number of papers to analyse is `` `r n_papers` ``.

There are `` `r n_md` `` distinct mental disorders (out of 25). About `r percent(n_yes_dsm5/n_papers)` (N=`r n_yes_dsm5`) are categorised according to Section II of [DSM-5 manual](https://dsm.psychiatryonline.org/doi/book/10.1176/appi.books.9780890425596). About `r percent(n_no_dsm5/n_papers)` (N=`r n_no_dsm5`) are 23-Dual, 24-Multiple or 25-Suicidal behavior disorder/nonsuicidal self-injury. In the following analysis, categories 23 and 24 are merged into a new one: 26-Various. Therefore, dual and multiple disorders are jointly treated.


\newpage

## Key figures

* *IN*: It is included in the paper
* *IN, PRODUCTION*: It is (almost) in final form
* *IN, DRAFT*: It is a exploratory figure. Aesthetics is not considered yet.
* *OUT*: It is not included in the paper.

### Figure 1 (IN, PRODUCTION)

Proportional stacked area chart: Temporal distribution of papers colored by assessment type. The sum of each year is always equal to hundred, and the value of each group (assessment type) is in percentages.


```{r key_plot_1_areachart, echo=FALSE, dpi=600, fig.width=12, fig.asp=0.65}
cols <- c("md", "md_id", "md_desc", "val_asstype", "year")

data_kp_areachart <- 
    all_data %>%
    select(cols)

data_kp_areachart$val_asstype <- fct_relevel(data_kp_areachart$val_asstype, c("NO", "OTHERS", "EFFICACY AND OTHERS", "EFFICACY"))

data_kp_areachart <- 
    data_kp_areachart %>%
    group_by(year, val_asstype) %>%  # first create counts for each group
    summarise(number_cases = n()) %>%
    mutate(total_cases_per_year = sum(number_cases),
           proportion = number_cases/total_cases_per_year,
           proportion_lbl = paste0(round(proportion*100,1), "%"))


# Not run
# display.brewer.all()
# display.brewer.pal(n = 6, name = "PRGn")
# brewer.pal(n = 6, name = "PRGn")[2:5]

# divergent palette instead of categorical (Set2). Get rid of edge values to avoid sharp contrast
pal <- brewer.pal(n = nlevels(data_kp_areachart$val_asstype)+2, name = "PRGn")[2:5]
pal <- c("#762A83", "#D9F0D3", "#7FBF7B", "#1B7837")

kp_areachart <- 
    data_kp_areachart %>%
        ggplot(aes(x=year, y=proportion, fill=val_asstype)) + 
        geom_area() +
        labs(title="Temporal distribution of papers per assessment type",
        x="Year", 
        y="Percentage of paper  per assessment type", 
        caption="Source: authors") + 
        guides(fill=guide_legend(title="Assessment")) + # modify legend title
        scale_fill_manual(values = pal) +
        scale_y_continuous(expand=c(0,0), labels=scales::percent_format(accuracy = 1), breaks=seq(0, 1.00, by=0.20), limits=c(0, 1.00)) +
        theme_minimal() +
        theme(legend.title = element_text(size=11), 
              legend.position = "bottom",
              legend.background = element_rect(color = "darkgray", size = 0.5, linetype ="solid"),
              legend.key = element_blank()) +
        # Change the line type and color of axis lines
        theme(axis.line = element_line(colour = "darkgray", size = 0.5, linetype = "solid")) +
        theme(panel.grid.major = element_blank()) + 
        theme(panel.grid.minor = element_blank()) +
        theme(panel.background = element_blank()) +
        theme(plot.margin=unit(rep(20, 4), "pt"))

kp_areachart
kp_file_name <- "fig1_areachart.png"
ggsave(plot = kp_areachart, filename = kp_file_name, device = "png", path = here::here("figs"),
    scale = 1, width = 20, height = 12, units = "cm", dpi = 600)

```


\newpage

### Figure 2 (OUT)

Stacked barchart: Distribution of papers per mental disorders, colored by assessment type.


```{r key_plot_2_barchart_stack, echo=FALSE, dpi=600, fig.width=12, fig.asp=0.65}
cols <- c("md", "md_id", "md_desc", "val_asstype")
data_kp_barchart <- 
    all_data %>%
    select(cols)

data_kp_barchart <- 
    data_kp_barchart %>% 
        group_by(md_id, md_desc, val_asstype) %>%  # first create counts for each group
        summarise(number_cases = n()) %>%
        mutate(proportion = number_cases/n_papers) %>% 
        ungroup() %>%
        group_by(md_id) %>%
        mutate(total_cases = sum(number_cases),
               proportion_sum = sum(proportion),
               proportion_lbl = paste0(round(proportion_sum*100,1), "%")) %>% 
        ungroup() %>%
        arrange(desc(proportion_sum), md_id)

# convert to factor to retain sorted order in plot.
data_kp_barchart$md_desc <- factor(data_kp_barchart$md_desc, levels=unique(data_kp_barchart$md_desc))  

data_kp_barchart$val_asstype <- fct_relevel(data_kp_barchart$val_asstype, c("NO", "OTHERS", "EFFICACY AND OTHERS", "EFFICACY"))

# Not run
# display.brewer.all()
# display.brewer.pal(n = 6, name = "PRGn")
# brewer.pal(n = 6, name = "PRGn")[2:5]

# divergent palette instead of categorical (Set2). Get rid of edge values to avoid sharp contrast
pal <- brewer.pal(n = nlevels(data_kp_barchart$val_asstype)+2, name = "PRGn")[2:5]
pal <- c("#762A83", "#D9F0D3", "#7FBF7B", "#1B7837")

kp_barchart <- 
    data_kp_barchart %>%
      ggplot(aes(x=md_desc, y=number_cases, label=number_cases)) + #, fill=val_ass, group= val_ass)) +
        geom_bar(stat="identity", aes(fill=val_asstype), position = position_stack(reverse = T)) +
        geom_text(aes(label=number_cases, group=val_asstype), size=2, nudge_y=0.2) +
        labs(title=paste0("Distribution of papers per mental disorder (N=",n_papers,")"),
             x="Mental disorders", 
             y="Number of cases", 
             caption="Source: authors") + 
        coord_flip() +
        guides(fill=guide_legend(title="Assessment")) +  # modify legend title
        # scale_fill_brewer(palette = pal) + # Set2
        scale_fill_manual(values = pal) + 
        scale_y_continuous(expand=c(0,0), breaks=seq(0, 22, by=2), limits=c(0, 22)) +
        theme_minimal()  +
        # Legend: Top-Right Inside the Plot") 
        theme(legend.title = element_text(size=11), 
              legend.justification = c('right', 'top'),
              legend.position=c(0.95, 0.95),  
              #legend.background = element_blank(),
              legend.background = element_rect(color = "darkgray", size = 0.5, linetype ="solid"),
              legend.key = element_blank()) +
        # Change the line type and color of axis lines
        theme(axis.line = element_line(colour = "darkgray", size = 0.5, linetype = "solid")) +
        theme(panel.grid.major = element_blank()) + 
        theme(panel.grid.minor = element_blank()) +
        theme(panel.background = element_blank()) +
        theme(plot.margin=unit(rep(20, 4), "pt"))

kp_barchart
kp_file_name <- "fig2_barchart_stack.png"
ggsave(plot = kp_barchart, filename = kp_file_name, device = "png", path = here::here("figs"),
    scale = 1, width = 20, height = 12, units = "cm", dpi = 600)

```


### Figure 2 (IN, PRODUCTION)

Proportional (stacked) barchart: Distribution of papers per mental disorders, colored by assessment type. Note that we draw two main colors in the legend: purple represents no assessment at all, the range of greens denotes distinct types of assessment.

```{r key_plot_2_barchart_dodge, echo=FALSE,dpi=600,fig.width=12,fig.asp=0.65}
cols <- c("md", "md_id", "md_desc", "val_asstype")

data_kp_barchart <- 
    all_data %>%
    select(cols)

data_kp_barchart <- 
    data_kp_barchart %>% 
        group_by(md_id, md_desc, val_asstype) %>%  # first create counts for each group
        summarise(number_cases = n()) %>%
        mutate(proportion = number_cases/n_papers) %>% 
        ungroup() %>%
        group_by(md_id) %>%
        mutate(total_cases = sum(number_cases),
               proportion_sum = sum(proportion),
               proportion_lbl = paste0(round(proportion_sum*100,1), "%")) %>% 
        ungroup() %>%
        arrange(desc(proportion_sum), md_id)

# convert to factor to retain sorted order in plot.
data_kp_barchart$md_desc <- factor(data_kp_barchart$md_desc, levels=unique(data_kp_barchart$md_desc))  

# Keep MD order equal for all other charts
md_all_ordered <- levels(data_kp_barchart$md_desc)

data_kp_barchart$val_asstype <- fct_relevel(data_kp_barchart$val_asstype, c("NO", "OTHERS", "EFFICACY AND OTHERS", "EFFICACY"))


# Not run
# display.brewer.all()
# display.brewer.pal(n = 7, name = "PRGn")
# brewer.pal(n = 7, name = "PRGn")
# divergent palette instead of categorical (Set2). Get rid of edge values to avoid sharp contrast
pal <- brewer.pal(n = nlevels(data_kp_barchart$val_asstype), name = "PRGn")
pal <- c("#762A83", "#D9F0D3", "#7FBF7B", "#1B7837")

lbls <- distinct(data_kp_barchart, md_desc, proportion_sum, proportion_lbl)

top_proportion <- sum(lbls[1:6, "proportion_sum"]) 
top_lbl <- paste0(round(top_proportion*100,1), "%")

kp_barchart <- 
    data_kp_barchart %>%
      ggplot(aes(x=md_desc, y=proportion)) + 
        # Uncomment  for stacked barchart (option A) 
        geom_bar(stat="identity", aes(fill=val_asstype)) +
        # Uncomment  for dodge barchart, single (option B) 
        # geom_bar(stat="identity", aes(fill=val_asstype), position=position_dodge(preserve = "single")) + 
        labs(title=paste0("Distribution per mental disorder and assessment (N=",n_papers,")"), 
             subtitle = "Total percentatge per mental disorder within each point",
             x="Mental disorders", 
             y="Percentatge of papers [%]", 
             caption="Source: authors") + 
        geom_segment(aes(x=md_desc, y=0, xend=md_desc, yend=proportion_sum), color="white") + # grey50
        geom_point(aes(y=proportion_sum), size=6, color="white") +  # lightgray
        # Percentatge inside point
        annotate("text", x = lbls$md_desc, y = lbls$proportion_sum,
                 label = lbls$proportion_lbl, color = "black", size=2, hjust = 0.4, vjust = 0.2) +
        # Arrow to indidate  Top6 mental disorders 
        annotate("text", x = "Schizophrenia spectrum and other psychotic disorders", y = .17,
                 label = top_lbl, color = "black", size = 3, hjust = -0.1, vjust = 1.2) +
        geom_segment(aes(x = "Schizophrenia spectrum and other psychotic disorders", 
                         xend = "Substance-related and addictive disorders", 
                         y = .19, 
                         yend = .19),
                         arrow = arrow(length = unit(0.5,"cm")), color = "black") +
        geom_segment(aes(x="Schizophrenia spectrum and other psychotic disorders", 
                         y=0.16, 
                         xend="Schizophrenia spectrum and other psychotic disorders", 
                         yend=0.19), color="black") +
        coord_flip() +
        guides(fill=guide_legend(title="Assessment")) +  # modify legend title
        # scale_fill_brewer(palette = "Set2") +
        scale_fill_manual(values = pal) + 
        scale_y_continuous(expand=c(0,0), labels=scales::percent_format(accuracy = 1), breaks=seq(0, 0.21, by=0.02), limits=c(0, 0.21)) +
        theme_minimal()  +
        # Legend: Top-Right Inside the Plot") 
        theme(legend.title = element_text(size=11), 
              legend.justification = c('right', 'top'),
              legend.position=c(0.95, 0.95),  
              #legend.background = element_blank(),
              legend.background = element_rect(color = "darkgray", size = 0.5, linetype ="solid"),
              legend.key = element_blank()) +
        # Change the line type and color of axis lines
        theme(axis.line = element_line(colour = "darkgray", size = 0.5, linetype = "solid")) +
        theme(panel.grid.major = element_blank()) + 
        theme(panel.grid.minor = element_blank()) +
        theme(panel.background = element_blank()) +
        theme(plot.margin=unit(rep(20, 4), "pt"))

kp_barchart
kp_file_name <- "fig2_barchart_dodge_a.png"
ggsave(plot = kp_barchart, filename = kp_file_name, device = "png", path = here::here("figs"),
    scale = 1, width = 21, height = 20, units = "cm", dpi = 600)


```


```{r echo=FALSE}
# TODO https://stackoverflow.com/questions/45055661/combine-grouped-and-stacked-bar-graph-in-r thanks
#- Add a new column (factor): No is value A, thre rest thre are B
#- use facet_wrap() over this new factor.  
# cols <- c("md", "md_id", "md_desc", "val_asstype", "val_ass")
# 
# data_kp_barchart <- 
#     all_data %>%
#     select(cols)
# 
# data_kp_barchart$val_asstype <- fct_relevel(data_kp_barchart$val_asstype, c("NO", "OTHERS", "EFFICACY AND OTHERS", "EFFICACY"))
# 
# data_kp_barchart <- 
#     data_kp_barchart %>% 
#         group_by(md_id, md_desc, val_asstype, val_ass) %>%  # first create counts for each group
#         summarise(number_cases = n()) %>%
#         mutate(proportion = number_cases/n_papers) %>% 
#         ungroup() %>%
#         group_by(md_id) %>%
#         mutate(total_cases = sum(number_cases),
#                proportion_sum = sum(proportion),
#                proportion_lbl = paste0(round(proportion_sum*100,1), "%")) %>% 
#         ungroup() %>%
#         arrange(desc(proportion_sum), md_id)
# 
# # convert to factor to retain sorted order in plot.
# data_kp_barchart$md_desc <- factor(data_kp_barchart$md_desc, levels=unique(data_kp_barchart$md_desc))  
# 
# kp_barchart <- 
#     data_kp_barchart %>%
#     ggplot(aes(x=val_ass, y=proportion)) + 
#     geom_bar(stat="identity", aes(fill=val_asstype), position="stack") + 
#         # Uncomment  for dodge barchart, single (option C) 
#         #geom_bar(stat="identity", aes(fill=val_asstype), position = position_dodge(preserve = "total")) + 
#     facet_wrap(~md_desc, ncol = 1) + theme(panel.spacing = unit(0, "lines")) +
#     coord_flip()

```

\newpage

### Figure 3 (IN, PRODUCTION)

Linechart: Distribution of papers (Total and top6 mental disorders) per year.


```{r key_plot_3_linechart, echo=FALSE, dpi=600, fig.width=12, fig.height=14, fig.asp=0.65}

top <- levels(all_data$md)[1:6]

prediction_2018 <- 52

data_total_byyear <- 
    all_data %>% 
    group_by(year) %>%  # first create counts for each group
    summarise(number_cases = n()) %>%
    mutate(md_desc = c("All"))


data_top_byyear <- 
    all_data %>%
      filter(md %in% top) %>%
      group_by(md_desc, year) %>%
      summarise(number_cases = n()) %>%
      bind_rows(data_total_byyear) %>%
      ungroup() %>%
      mutate(md_desc = factor(md_desc)) %>%
      arrange(desc(number_cases))

# https://www.r-graph-gallery.com/portfolio/ggplot2-package/
# https://ggplot2.tidyverse.org/reference/position_stack.html

data_top_byyear$md_desc <- fct_relevel(data_top_byyear$md_desc, 
                                       c("All", "Depressive disorders", "Various", "Anxiety disorders", 
                                         "Trauma and stressor-related disorders",
                                         "Substance-related and addictive disorders",
                                         "Schizophrenia spectrum and other psychotic disorders"))
brks <- levels(data_top_byyear$md_desc) 
    
kp_linechart <-
    data_top_byyear %>%
        ggplot(aes(x=year, y=number_cases, group=md_desc)) +
        geom_vline(aes(xintercept = 2017), color="lightgray", linetype = "dashed", size = 0.5) +
        annotate("rect", xmin = 2017, xmax = 2018, ymin = -Inf, ymax = +Inf, fill = "lightgray", alpha = 0.2) +
        geom_line(aes(color=md_desc), size=1, alpha=.4) +
        # prediction all papers in 2018
        geom_segment(aes(x=2017,
                         y=39,
                         xend=2018,
                         yend=prediction_2018), color="darkgray", linetype=2) +
        geom_point(aes(color=md_desc), size=6) +
        labs(title="Distribution top mental disorders per year", 
             subtitle = paste0("All vs. top mental disorders (", top_lbl,"). Dashed line denotes extrapolation for 2018"),
             x="Year", 
             y="Number of cases", 
             caption="Source: authors") + 
        scale_color_brewer(palette="Set2", breaks=brks) +
        geom_text(aes(label = number_cases), color= "white", size=3) +
        # prediction all papers in 2018
        # geom_point(x=2018, y=prediction_2018, color="darkgray", size=6) +
        # annotate("text", x =2018, y = prediction_2018,
        #          label = prediction_2018, color = "black", size=3) +
        theme_minimal() +
        theme(legend.title = element_blank()) +
        # Legend: Top-Right Inside the Plot") 
        theme(legend.justification = c('left', 'top'),
              legend.position=c(0.05, 0.95),  
              #legend.background = element_blank(),
              legend.background = element_rect(color = "darkgray", size = 0.5, linetype ="solid"),
              legend.key = element_blank()) +
        theme(panel.grid.major = element_blank()) + 
        theme(panel.grid.minor = element_blank()) +
        theme(panel.background = element_blank()) +
        theme(plot.margin=unit(rep(20, 4), "pt")) +
        # Change the line type and color of axis lines
        theme(axis.line = element_line(colour = "darkgray", size = 0.5, linetype = "solid"))

kp_linechart
kp_file_name <- "fig3_linechart.png"
ggsave(plot = kp_linechart, filename = kp_file_name, device = "png", path = here::here("figs"),
    scale = 1, width = 20, height = 18, units = "cm", dpi = 600) 


```

\newpage

### Figure 4 (OUT)

Table (Example 1): Distribution of papers (apps) per mental disorder.  _How many apps are related to each mental disorder?_ Per each mental disorder, assessment (yes/no) and year, we show the paper id and appname.


```{r key_plot_4_table1, echo=FALSE}

# library(formattable)

kp_file_name <- here::here("figs", "table1.html")
#' Example  1, verbose table
data_kp_apps <- 
    all_data %>%
    arrange(md_id, val_ass, year, id)

#' source: https://cran.r-project.org/web/packages/kableExtra/vignettes/awesome_table_in_html.html

# options(knitr.kable.NA = '-')
data_kp_apps %>%
    select(`Mental Disorder` = md,
           `Assessment` = val_ass,
           `Year` = year,
           `Paper id` = id,
           `App Name` = app_name) %>%
    kable(format="html", escape = T, booktabs = TRUE,
          caption =  paste0("Distribution of papers (apps) per mental disorder\n",
                            "'NA' is app not specified/available")) %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
    column_spec(1, bold = T) %>%
    collapse_rows(columns = 1:3, valign = "top") #%>%  
    # save_kable(file = kp_file_name, self_contained = T)

```

### Figure 4 (IN, DRAFT)

Table (Example 2): _Compact_ distribution of papers (apps) per mental disorder, grouping the references per app. The mumber(s) in brackets next to the app name is the reference(s) in which the app is mentioned. 


```{r key_plot_4_table2, echo=FALSE}

kp_file_name <- here::here("figs", "table2.html")

unite_paper_ids <- function(mentaldisorder, appname) {
    if (!is.na(appname)) {
        all_data %>% 
            filter(md_desc == mentaldisorder & app_name==appname) %>%
            arrange(year) %>%
            select(id) %>%
            as_vector() %>%
            stringr::str_c(collapse = ";")    
    } else {
         all_data %>% 
            filter(md_desc == mentaldisorder & is.na(app_name)) %>%
            arrange(year) %>%
            select(id) %>%
            as_vector() %>%
            stringr::str_c(collapse = ";")  
    }
}

data_kp_apps2 <- 
    all_data %>%
    group_by(md_desc, app_name) %>%
    summarise(number_apps = n()) %>% 
    arrange(number_apps, md_desc)

data_kp_apps2 <- 
    data_kp_apps2 %>%
    add_column(ids = purrr::map2(data_kp_apps2$md_desc, data_kp_apps2$app_name, unite_paper_ids))

data_kp_apps2 <- 
    data_kp_apps2 %>%
    add_column(app_ids = paste0(data_kp_apps2$app_name, " (", data_kp_apps2$ids, ")"))

data_kp_apps2 <- 
    data_kp_apps2 %>%
    group_by(md_desc) %>%
    summarise(app_ids_merge = paste0(app_ids, collapse = ", ")) 

data_kp_apps2$md_desc <- factor(data_kp_apps2$md_desc, levels=md_all_ordered)  


# options(knitr.kable.NA = '-')
data_kp_apps2 %>%
    select(`Mental Disorder` = md_desc,
           `References by app` = app_ids_merge) %>%
    kable(formt="html", escape = T, booktabs = TRUE,    
          caption = paste0("Compact distribution of papers (apps) per mental disorder\n", 
                            "'NA' is app not specified/available")) %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
    column_spec(1, bold = T) %>%
    collapse_rows(columns = 1, valign = "top") #%>%  
    # save_kable(file = kp_file_name, self_contained = T)


```


### Figure 4 (IN/OUT?, DRAFT)

Circular barplot (Example 3): Each cell means one occurence of the app in a paper.

```{r key_plot_4_table3, echo=FALSE}

#' source: https://www.r-graph-gallery.com/297-circular-barplot-with-groups/

data_kp_apps3 <- 
    all_data %>%
    filter(as.integer(md_id) != 26) %>%
    group_by(app_name, md_desc) %>%
    summarise(number_apps = n()) %>% 
    arrange(md_desc, number_apps)

data_kp_apps3$app_name <- fct_explicit_na(data_kp_apps3$app_name, "Not App Available")
data_kp_apps3$id <- seq(1, nrow(data_kp_apps3))


# source: https://www.r-bloggers.com/how-to-expand-color-palette-with-ggplot-and-rcolorbrewer/
n_colors <- length(unique(data_kp_apps3$md_desc))
get_palette <- colorRampPalette(brewer.pal(8, "Set1"))


# Get the name and the y position of each label
label_data=data_kp_apps3
number_of_bar=nrow(label_data)
angle= 90 - 360 * (label_data$id-0.5)/number_of_bar     # I substract 0.5 because the letter must have the angle of the center of the bars. Not extreme right(1) or extreme left (0)
label_data$hjust<-ifelse(angle < -90, 1, 0)
label_data$angle<-ifelse(angle < -90, angle+180, angle)


kp_circularbarplot <- 
    ggplot(data_kp_apps3, aes(x=as.factor(id), y=number_apps, fill=md_desc)) +  
      geom_bar(stat="identity", alpha=0.5) +
      # Lmits of the plot: The negative value controls the size of the inner circle, the positive one is useful to add size over each bar
      ylim(-5,10) +
      scale_fill_manual(values = get_palette(n_colors), name="Mental disorders") +
      scale_color_manual(values = get_palette(n_colors)) +    
      theme_minimal() +
      theme(
        legend.position = "right",
        legend.title = element_blank(),
        legend.text = element_text(size=5),
        axis.text = element_blank(),
        axis.title = element_blank(),
        panel.grid = element_blank(),
        plot.margin = unit(rep(-1,4), "cm")
      ) +
      guides (fill = guide_legend(ncol=1)) +    
      coord_polar(start=0) + 
      geom_text(data=label_data, aes(x=id, y=number_apps, label=app_name, hjust=hjust, color=md_desc), 
                alpha=0.6, size=3, angle= label_data$angle, inherit.aes = FALSE, show.legend = FALSE ) +
      geom_hline(yintercept = seq(1:10), col = "white", lwd=0.5)

kp_circularbarplot

kp_file_name <- "fig4_circularbarplot.png"
ggsave(plot = kp_circularbarplot, filename = kp_file_name, device = "png", path = here::here("figs"),
    scale = 1, width = 25, height = 25, units = "cm", dpi = "print") #300


```

```{r echo=FALSE}

#' circlize, source: http://jokergoo.github.io/circlize/example/bi_directional.html
# library(circlize)
# 
# appnames <- unique(data_kp_apps3$app_name)
# fappnames <- factor(data_kp_apps3$app_name, levels = appnames)    
# 
# circos.clear()
# circos.initialize(factors = fappnames, x = appnames)
# 
# factors = appnames[1:4] #letters[1:4]
# circos.initialize(factors = factors, xlim = c(0, 1))
# circos.track(ylim = c(0, 1), panel.fun = function(x, y) {
#     circos.points(1:20/20, 1:20/20)
# })
# text(0, 0, "This is\nthe center", cex = 1.5)
# legend("bottomleft", pch = 1, legend = "This is the legend")
# title("This is the title")
# 
# 
# col_fun = colorRamp2(c(-2, 0, 2), c("green", "yellow", "red"))
# 
# circlize_plot = function() {
#     set.seed(12345)
#     fa <- appnames[1:10]
#     n <- length(fa)
#     circos.initialize(factors = fa, xlim = c(0, 1))
#     circos.track(ylim = c(0, 1), panel.fun = function(x, y) {
#         circos.points(runif(20), runif(20), cex = 0.5, pch = 16, col = 2)
#         circos.points(runif(20), runif(20), cex = 0.5, pch = 16, col = 3)
#     })
#     circos.track(ylim = c(0, 1), panel.fun = function(x, y) {
#         circos.lines(sort(runif(20)), runif(20), col = 4)
#         circos.lines(sort(runif(20)), runif(20), col = 5)
#     })
# 
#     for(i in n) {
#         circos.link(sample(fa, 1), sort(runif(10))[1:2], 
#                     sample(fa, 1), sort(runif(10))[1:2],
#                     col = add_transparency(col_fun(rnorm(1))))
#     }
#     circos.clear()
# }
# 
# circlize_plot()
# 
# 
# 
# set.seed(999)
# mat <- matrix(sample(18, 18), 3, 6) 
# rownames(mat) <- paste0("S", 1:3)
# colnames(mat) <- paste0("E", 1:6)
# mat
# 
# 
# df <- data.frame(from = rep(rownames(mat), times = ncol(mat)),
#     to = rep(colnames(mat), each = nrow(mat)),
#     value = as.vector(mat),
#     stringsAsFactors = FALSE)
# 
# df
# 
# 
# circos.par(start.degree = 90, track.margin = c(-0.1, 0.1), gap.degree = 4, points.overflow.warning = FALSE)
# chordDiagram(df)
# circos.clear()


```

\newpage

### Figure 5 (IN, DRAFT) - ONGOING

Bubble plot: Distribution of papers per mental disorder and technology variables (sensor capabilities and features)

In the following, some exploratory charts are shown on the way to reach the bubble plot, which is the last chart. None of the following charts are in production stage, only drafted. Please, do not pay much attention to the color palette and aesthetics yet.

```{r key_plot_5_sens, echo=FALSE, dpi=600, fig.width=12, fig.height=14, fig.asp=0.65}
# Sensory capabilities related to each mental disorder 
cols = c("id", "md", "md_id", "md_desc", 
         "sens_acc", "sens_gyr", "sens_gps", "sens_mic", "sens_cam",
         "os_ios", "os_and", "app_name",
         "type", "year")
cols_sens <- c("sens_acc", "sens_gyr", "sens_gps", "sens_mic", "sens_cam")

n_sens <- 
    all_data %>%
    select(cols_sens) %>%
    filter((sens_acc=="YES") | (sens_gyr=="YES") | (sens_gps=="YES") | 
              (sens_mic=="YES") | (sens_cam=="YES")) %>%
    nrow()

all_data %>%
    select(cols) %>%
    gather(cols_sens, key="sens_type", value="sens_value") %>%
    ggplot(aes(x=md_desc)) +
    geom_bar(stat="count", aes(fill=factor(sens_value))) +
    coord_flip() +
    facet_wrap(~sens_type)


```


`r percent(n_sens/n_papers)` of papers use **at least** a sensing capability (N=`r n_sens`). The use of the acc and gyr is residual; gps and mic are more significant, but in a low proportion: gps = `r percent(nrow(filter(all_data, sens_gps=="YES"))/n_papers)`, mic = `r percent(nrow(filter(all_data, sens_mic=="YES"))/n_papers)`, cam = `r percent(nrow(filter(all_data, sens_cam=="YES"))/n_papers)` . Note that some papers use both type of sensors, so the sum of percentages of gps, mic and cam exceeds the total percentage of papers that use **at least** a sensing capability.



```{r key_plot_5_feat, echo=FALSE,dpi=600, fig.width=12, fig.height=14, fig.asp=0.65}
# features related to each mental disorder 
cols = c("id", "md", "md_id", "md_desc", 
         "feat_use", "feat_promp", "feat_soc", "feat_hcp", "feat_learn", 
         "feat_prog", "feat_ca", "feat_ass", "feat_vr", "feat_ar", "feat_pers", "feat_game",
         "os_ios", "os_and", "app_name",
         "type", "year")

cols_feat = c("feat_use", "feat_promp", "feat_soc", "feat_hcp", "feat_learn", 
              "feat_prog", "feat_ca", "feat_ass", "feat_vr", "feat_ar", "feat_pers", "feat_game")
n_feat <- 
    all_data %>%
    select(cols_feat) %>%
    filter((feat_use=="YES") || (feat_promp=="YES") || (feat_soc=="YES") || (feat_hcp=="YES") || 
           (feat_learn=="YES") || (feat_prog=="YES") || (feat_ca=="YES") || (feat_ass=="YES") || 
           (feat_vr=="YES") || (feat_ar=="YES") || (feat_pers="YES") || (feat_game="YES"))  %>%
    nrow()

all_data %>%
    select(cols) %>%
    gather(cols_feat, key="feat_type", value="feat_value") %>%
    ggplot(aes(x=md_desc)) +
    geom_bar(stat="count", aes(fill=factor(feat_value))) +
    coord_flip() +
    facet_wrap(~feat_type)

```

`r percent(n_feat/n_papers)` of papers provide/offer/use **at least** a feature capability (N=`r n_feat`). 



```{r key_plot_5_anal, echo=FALSE,dpi=600, fig.width=12, fig.height=14, fig.asp=0.65}
# analytics support related to each mental disorder 
cols = c("id", "md", "md_id", "md_desc", 
         "anal_ml", "anal_beh", "anal_act", "anal_sen", "anal_sp", 
         "os_ios", "os_and", "app_name",
         "type", "year")

cols_anal = c("anal_ml", "anal_beh", "anal_act", "anal_sen", "anal_sp")
n_anal <- 
    all_data %>%
    select(cols_anal) %>%
    filter((anal_ml=="YES") | (anal_beh=="YES") | (anal_act=="YES") | (anal_sen=="YES") | (anal_sp=="YES"))  %>%
    nrow()

all_data %>%
    select(cols) %>%
    gather(cols_anal, key="anal_type", value="anal_value") %>%
    ggplot(aes(x=md_desc)) +
    geom_bar(stat="count", aes(fill=factor(anal_value))) +
    coord_flip() +
    facet_wrap(~anal_type)
```


`r percent(n_anal/n_papers)` of papers implement/use **at least** advanced analytics (N=`r n_anal`). 



```{r key_plot_5_sens_bubblechart, echo=FALSE, warning=FALSE, dpi=600, fig.width=12, fig.height=14, fig.asp=0.65}
cols = c("id", "md_id", "md_desc", 
         "sens_acc", "sens_gyr", "sens_gps", "sens_mic", "sens_cam",
         "os_ios", "os_and", "app_name",
         "type", "year")
cols_sens <- c("sens_acc", "sens_gyr", "sens_gps", "sens_mic", "sens_cam")
data_kp_sens <-
    all_data %>%
    select(cols) %>%
    gather(cols_sens, key="sens_type", value="sens_value") %>%
    mutate(cat = "sens") %>%
    filter(sens_value == "YES") %>%
    group_by(md_desc, sens_type, cat) %>%
    summarise(number_cases = n()) %>%
    ungroup() # required to add_row() 

md_sens <- unique(data_kp_sens$md_desc)
md_dif <- setdiff(md_all_ordered, md_sens)
if (length(md_dif) > 0) {
    for (md in md_dif) {
        # Added "sens_mic" (or any other values) to avoid NA in the "sens_type" variable. Nothing is drawn in the plot
        data_kp_sens <- add_row(data_kp_sens, md_desc=md, sens_type="sens_mic", cat="sens")
    }
}

data_kp_sens$md_desc <- fct_relevel(data_kp_sens$md_desc, levels=md_all_ordered)

data_kp_sens %>%
    ggplot(aes(x=md_desc, y=sens_type)) +
    geom_point(aes(colour=sens_type, size=number_cases), na.rm = TRUE) + 
    geom_text(aes(label=number_cases), size=3, na.rm = TRUE) +
    scale_size_area(max_size=10) +
    coord_flip()

```



```{r key_plot_5_feat_bubblechart, echo=FALSE, dpi=600, fig.width=12, fig.height=14, fig.asp=0.65}
cols = c("id", "md_id", "md_desc", 
         "feat_use", "feat_promp", "feat_soc", "feat_hcp", "feat_learn", 
         "feat_prog", "feat_ca", "feat_ass", "feat_vr", "feat_ar", "feat_pers", "feat_game",
         "os_ios", "os_and", "app_name",
         "type", "year")

cols_feat = c("feat_use", "feat_promp", "feat_soc", "feat_hcp", "feat_learn", 
              "feat_prog", "feat_ca", "feat_ass", "feat_vr", "feat_ar", "feat_pers", "feat_game")

data_kp_feat <- 
    all_data %>%
    select(cols) %>%
    gather(cols_feat, key="feat_type",value="feat_value") %>%
    mutate(cat = "feat") %>%
    filter(feat_value == "YES") %>%
    group_by(md_desc, feat_type, cat)  %>%
    summarise(number_cases = n())  %>%
    ungroup() # required to add_row() 

md_feat <- unique(data_kp_feat$md_desc)
md_dif <- setdiff(md_all_ordered, md_feat)
if (length(md_feat) > 0) {
    for (md in md_dif) {
        # Added "feat_use" (or any value) to avoid NA in the "feat_type" variable. Nothing is drawn in the plot
        data_kp_feat <- add_row(data_kp_feat, md_desc=md, feat_type="feat_use", cat="feat")
    }
}

data_kp_feat$md_desc <- factor(data_kp_feat$md_desc, levels=md_all_ordered)  

data_kp_feat %>%
    ggplot(aes(x=md_desc, y=feat_type)) +
    geom_point(aes(colour=feat_type, size=number_cases)) + 
    geom_text(aes(label=number_cases), size=3) +
    scale_size_area(max_size=15) +
    coord_flip()

```


```{r key_plot_5_anal_bubblechart, echo=FALSE, dpi=600, fig.width=12, fig.height=14, fig.asp=0.65}
cols = c("id", "md", "md_id", "md_desc", 
         "anal_ml", "anal_beh", "anal_act", "anal_sen", "anal_sp", 
         "os_ios", "os_and", "app_name",
         "type", "year")

cols_anal = c("anal_ml", "anal_beh", "anal_act", "anal_sen", "anal_sp")

data_kp_anal <- 
    all_data %>%
    select(cols) %>%
    gather(cols_anal, key="anal_type",value="anal_value") %>%
    mutate(cat = "anal") %>%
    filter(anal_value == "YES") %>%
    group_by(md_desc, anal_type, cat)  %>%
    summarise(number_cases = n())  %>%
    ungroup() # required to add_row() 

md_anal <- unique(data_kp_anal$md_desc)
md_dif <- setdiff(md_all_ordered, md_anal)
if (length(md_anal) > 0) {
    for (md in md_dif) {
        # Added "anal_ml" (or any value) to avoid NA in the "anal_type" variable. Nothing is drawn in the plot
        data_kp_anal <- add_row(data_kp_anal, md_desc=md, anal_type="anal_ml", cat="anal")
    }
}

# Since the behavior analysis is not compatible with any article, I add this line so that "anal_sen" appears in the graph.
data_kp_anal <- add_row(data_kp_anal, md_desc="Various", anal_type="anal_sen", cat="anal")


data_kp_anal$md_desc <- factor(data_kp_anal$md_desc, levels=md_all_ordered)  

data_kp_anal %>%
    ggplot(aes(x=md_desc, y=anal_type)) +
    geom_point(aes(colour=anal_type, size=number_cases), na.rm = TRUE) + 
    geom_text(aes(label=number_cases), size=3, na.rm = TRUE) +
    scale_size_area(max_size=15) +
    coord_flip()
```


This is the final bubble plot. 

```{r key_plot_5_bubblechart, echo=FALSE, dpi=600, fig.width=15, fig.height=14, fig.asp=0.65}
data_kp_sens <-
    data_kp_sens %>%
    rename(tech_type=sens_type)

data_kp_feat <-
    data_kp_feat %>%
    rename(tech_type=feat_type)

data_kp_anal <-
    data_kp_anal %>%
    rename(tech_type=anal_type)

data_kp_all <-
    bind_rows(data_kp_feat, data_kp_sens, data_kp_anal)


kp_bubblechart <- 
    data_kp_all %>%
    ggplot(aes(x=md_desc, y=tech_type)) +
    geom_point(aes(colour=cat, size=number_cases), na.rm = TRUE, show.legend = FALSE) + 
    geom_text(aes(label=number_cases), size=3, na.rm = TRUE) +
    scale_size_area(max_size=15) +
    coord_flip() +
    theme(axis.text.x=element_text(angle = 60))


kp_bubblechart
library(ggExtra)
ggMarginal(p=kp_bubblechart,  type = "histogram", fill="transparent")


kp_file_name <- "fig5_bubblechart.png"
ggsave(plot = kp_bubblechart, filename = kp_file_name, device = "png", path = here::here("figs"),
    scale = 1, width = 35, height = 20, units = "cm", dpi = 600)



```


