---
title: 'Analysis and visualisations for "Smartphone apps for the treatment of mental disorders: a systematic review"'
author: "Carlos Granell et al."
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    df_print: paged
    toc: yes
urlcolor: blue    
---

## License

This document is licensed under a [Creative Commons Attribution 4.0 International License](https://creativecommons.org/licenses/by/4.0/).

All contained code is licensed under the [Apache License 2.0](https://choosealicense.com/licenses/apache-2.0/).

The data used is licensed under a [Open Data Commons Attribution License](https://opendatacommons.org/licenses/by/).

See the paper's "Author Contributions" section for details on the contributors of data files.

\newpage


## Metadata

Required libraries and runtime environment description.

```{r load_libraries, echo=FALSE, message=FALSE, warning=FALSE}
library(here)
library(emidata)
library(tidyverse)
library(tidytext)
library(kableExtra)
library(stringr)
library(skimr)
# library(ggalt)
library(scales)
library(RColorBrewer)
library(gridExtra)
#library(treemap)
library(forcats)
library(purrr)
library(cowplot)    # publication-ready theme for ggplot2
#library(hrbrthemes)  # TODO: see https://stackoverflow.com/questions/14733732/cant-change-fonts-in-ggplot-geom-text to solve font does not find

```


```{r session_info, echo=FALSE}
devtools::session_info(include_base = TRUE)
```

This document is versioned in a public [git](https://git-scm.com/) repo: [https://github.com/cgranell/emi-mhealth](https://github.com/cgranell/emi-mhealth).

\newpage

This R notebook contains the code to produce the final figures and tables of the paper. 

## Data 

Input datasets are the processed datasets within the *emidata* data package. The package code is available in a public [git](https://git-scm.com/) repo: [https://github.com/cgranell/emidata](https://github.com/cgranell/emidata). We analyse the follwing three datasets of the *emidata* package: 

* *ipapers2018_psydata* (extracted data items related to psychology) has `` `r nrow(ipapers2018_psydata)` `` records and `` `r ncol(ipapers2018_psydata)` `` columns.
* *ipapers2018_csdata* (extracted data items related to tech/cs) has `` `r nrow(ipapers2018_csdata)` `` records and `` `r ncol(ipapers2018_csdata)` `` columns. 
* *ipapers2018* (list of analysed papers) has `` `r nrow(ipapers2018)` `` records and `` `r ncol(ipapers2018)` `` columns.


```{r all_data, echo=FALSE}

cs_data <- ipapers2018_csdata
psy_data <- ipapers2018_psydata

all_data <- psy_data %>%
    inner_join(cs_data, by="id")

# Drop "included" columns
all_data <- all_data %>% select(-id_csin, -id_psyin)

all_data <- all_data %>%
    inner_join(ipapers2018, by="id") %>%
    select(-filename, -title, -abstract, -journal, -author, -keywords)

# cast to factor
all_data$md <- factor(all_data$md, levels=names(sort(table(all_data$md), decreasing=T)))
all_data$val_asstype <- factor(all_data$val_asstype)


#' Replace existing factors levels
levels(all_data$md)[levels(all_data$md)=="23-Duo-comorbid"] <- "23-Comorbid disorders"
levels(all_data$md)[levels(all_data$md)=="24-Multiple"] <- "24-Various disorders"
levels(all_data$val_asstype)[levels(all_data$val_asstype)=="NO"] <- "NO ASSESSMENT"
levels(all_data$val_asstype)[levels(all_data$val_asstype)=="EFFECT AND USABILITY/USER EXPERIENCE"] <- "EFFECT AND USABILITY/UX"
levels(all_data$val_asstype)[levels(all_data$val_asstype)=="USABILITY/USER EXPERIENCE"] <- "USABILITY/UX"

# all_data$md <- fct_other(all_data$md, drop=c("23-Duo-comorbid", "24-Multiple"), 
#                          other_level = c("23-Comorbid disorders","24-Various disorders"))

#' Adjust readibily of long description of mental disorders for production plot
levels(all_data$md)[levels(all_data$md)=="6-Obsessive-Compulsive and related disorders"] <- "6-Obsessive-Compulsive and\n related disorders"
levels(all_data$md)[levels(all_data$md)=="25-Suicidal behavior disorder/nonsuicidal self-injury"] <- "25-Suicidal behavior disorder/\nnonsuicidal self-injury"
levels(all_data$md)[levels(all_data$md)=="2-Schizophrenia spectrum and other psychotic disorders"] <- "2-Schizophrenia spectrum and\n other psychotic disorders"
levels(all_data$md)[levels(all_data$md)=="16-Substance-related and addictive disorders"] <- "16-Substance-related and\n addictive disorders"
levels(all_data$md)[levels(all_data$md)=="7-Trauma and stressor-related disorders"] <- "7-Trauma and\n stressor-related disorders"

#' Sync changes of "md" to other two columns, "md_id"" and "md_desc""
all_data <- 
    all_data %>% 
        separate(md, c("md_id","md_desc"), "-", extra="merge", remove=FALSE)

all_data$md <- factor(all_data$md, levels=names(sort(table(all_data$md), decreasing=T)))

category_levels <- c("YES","NO")
all_data <- 
    all_data %>%
    mutate(md_dsm5 = factor(if_else(md_id <= 22, "YES", "NO"), levels=category_levels))

```

\newpage


## Descriptive statistics

```{r stats, echo=FALSE}

n_md <- nlevels(all_data$md)
n_papers = nrow(all_data)
n_dsm5_yes <- nrow(filter(all_data, md_dsm5 == "YES"))
n_dsm5_no <- nrow(filter(all_data, md_dsm5 == "NO"))

n_assessment_yes <- nrow(filter(all_data, val_ass == "YES"))
n_assessment_no <- nrow(filter(all_data, val_ass == "NO"))

n_assessment_effect <- nrow(filter(all_data, val_asstype=="EFFECT"))
n_assessment_effectux <-nrow(filter(all_data, val_asstype=="EFFECT AND USABILITY/UX"))
n_assessment_ux <-nrow(filter(all_data, val_asstype=="USABILITY/UX"))


# Keep the order of mental disorder equal for all charts 
temp_for_order <- 
    all_data %>% 
    group_by(md_id, md_desc) %>%
    summarise(number_cases = n()) %>%
    mutate(proportion = number_cases/n_papers) %>% 
    arrange(desc(proportion), md_id) 

# convert to factor to retain sorted order of mendata diorders 
temp_for_order$md_desc <- factor(temp_for_order$md_desc, levels=unique(temp_for_order$md_desc))  

# Keep MD order equal for all other charts
md_all_ordered <- levels(temp_for_order$md_desc)


```

The final number of papers to analyse is `r n_papers`.

There are `r n_md` distinct mental disorders (out of 25). About `r percent(n_dsm5_yes/n_papers)` (N=`r n_dsm5_yes`) are categorised according to Section II of [DSM-5 manual](https://dsm.psychiatryonline.org/doi/book/10.1176/appi.books.9780890425596). About `r percent(n_dsm5_no/n_papers)` (N=`r n_dsm5_no`) are _23-Comorbid disorders_, _24-Various disorders_ or _25-Suicidal behavior disorder/nonsuicidal self-injury_.

About `r percent(n_assessment_yes/n_papers)` (N=`r n_assessment_yes`) of papers reported some kind of assessment, whereas `r percent(n_assessment_no/n_papers)` (N=`r n_assessment_no`) reported no assessment at all. Looking closer at the type of assessment: `r percent(n_assessment_effect/n_papers)` (N=`r n_assessment_effect`) focus on the effect of intervention on clinical symptomology; `r percent(n_assessment_effectux/n_papers)` (N=`r n_assessment_effectux`) report a mix of effect and usability / UX assessment; `r percent(n_assessment_ux/n_papers)` (N=`r n_assessment_ux`) focus solely on usability / UX.


\newpage

## Key figures

* *IN*: It is included in the paper
* *IN, PRODUCTION*: It is (almost) in final form
* *IN, DRAFT*: It is a exploratory figure. Aesthetics is not considered yet.
* *OUT*: It is not included in the paper.

### Figure 2. Temporal distribution of papers per assessment type

Temporal distribution of papers colored by assessment type. It is a proportional stacked area chart in which the sum of each year is always equal to hundred, and the value of each group (assessment type) is in percentages.


```{r fig2_tempdist, echo=FALSE, dpi=600, fig.width=10, fig.height=22, fig.asp=1}
cols <- c("md", "md_id", "md_desc", "val_asstype", "year")

data_plot_tempdist <- 
    all_data %>%
    select(cols)

data_plot_tempdist$val_asstype <- fct_relevel(data_plot_tempdist$val_asstype, 
                                             c("NO ASSESSMENT", "USABILITY/UX", "EFFECT AND USABILITY/UX", "EFFECT"))

data_plot_tempdist <- 
    data_plot_tempdist %>%
    group_by(year, val_asstype) %>%  # first create counts for each group
    summarise(number_cases = n()) %>%
    mutate(total_cases_per_year = sum(number_cases),
           proportion = number_cases/total_cases_per_year,
           proportion_lbl = paste0(round(proportion*100,1), "%"))

# Not run
# display.brewer.all()
#display.brewer.pal(n = 6, name = "PRGn")
# brewer.pal(n = 6, name = "PRGn")[2:5]

# divergent palette instead of categorical (Set2). Get rid of edge values to avoid sharp contrast
#pal <- brewer.pal(n = nlevels(data_plot_tempdist$val_asstype)+2, name = "PRGn")[2:5]
#pal <- c("#762A83", "#D9F0D3", "#7FBF7B", "#1B7837")
pal <- c("NO ASSESSMENT"="#AF8DC3", "USABILITY/UX"="#D9F0D3", "EFFECT AND USABILITY/UX"="#7FBF7B", "EFFECT"="#1B7837")


prediction_2018 <- 52


plot_tempdist_stakedbarchart <- 
    data_plot_tempdist %>%
        ggplot(aes(x=year, y=number_cases, fill=val_asstype)) + 
        geom_bar(stat="identity") +
        geom_text(aes(label=number_cases), size=2.5,position=position_stack(vjust = 0.5)) +
        labs(#title="Count of papers per year,, colored by assessment type", 
             x="", 
             y="# of papers") +
        scale_fill_manual(values = pal) +
        scale_x_continuous(breaks = seq(2013,2018, by=1)) +
        guides(fill="none") +
        # Prediction 2018
        annotate("rect", alpha = 0.2, 
            xmin = 2018 - 0.45, xmax = 2018 + 0.45,
            ymin = 13, ymax = prediction_2018, linetype="dashed") +
        theme_minimal() +
        # Change the line type and color of axis lines
        theme(axis.line = element_line(colour = "darkgray", size = 0.5, linetype = "solid")) +
        # theme(panel.grid.major = element_blank()) + 
        theme(panel.grid.minor = element_blank()) +
        theme(panel.background = element_blank()) +
        theme(plot.margin=unit(rep(20, 4), "pt"))

# plot_tempdist_stakedbarchart


plot_tempdist_areachart <- 
    data_plot_tempdist %>%
        ggplot(aes(x=year, y=proportion, fill=val_asstype)) + 
        geom_area() +
        labs(#title="Temporal distribution of papers per assessment type",
        x="Year", 
        y="Percentage of papers [%]", 
        caption="Source: authors") + 
        guides(fill=guide_legend(title="Assessment Type", nrow=2)) + # modify legend title
        scale_fill_manual(values = pal) +
        scale_y_continuous(expand=c(0,0), labels=scales::percent_format(accuracy = 1), breaks=seq(0, 1.00, by=0.20), limits=c(0, 1.00)) +
        theme_minimal() +
        theme(legend.title = element_text(size=11), 
              legend.position = "bottom",
              legend.background = element_rect(color = "darkgray", size = 0.5, linetype ="solid"),
              legend.key = element_blank()) +
        # Change the line type and color of axis lines
        theme(axis.line = element_line(colour = "darkgray", size = 0.5, linetype = "solid")) +
        theme(panel.grid.major = element_blank()) + 
        theme(panel.grid.minor = element_blank()) +
        theme(panel.background = element_blank()) +
        theme(plot.margin=unit(rep(20, 4), "pt"))

#plot_tempdist_areachart

plot_tempdist <- plot_grid(plot_tempdist_stakedbarchart, plot_tempdist_areachart, labels = c("A", "B"), ncol= 1, align = "v")#, axis = "left")
plot_tempdist

plot_tempdist_file_name <- "fig2_tempdist.png"
ggsave(plot = plot_tempdist, filename = plot_tempdist_file_name, device = "png", path = here::here("figs"),
     scale = 1, width = 20, height = 28, units = "cm", dpi = 600)

```


\newpage

### Figure 3 (OUT)

Stacked barchart: Distribution of papers per mental disorders, colored by assessment type.


```{r key_plot_2_barchart_stack, echo=FALSE, dpi=600, fig.width=12, fig.asp=0.65}
cols <- c("md", "md_id", "md_desc", "val_asstype")
data_kp_barchart <- 
    all_data %>%
    select(cols)

data_kp_barchart <- 
    data_kp_barchart %>% 
        group_by(md_id, md_desc, val_asstype) %>%  # first create counts for each group
        summarise(number_cases = n()) %>%
        mutate(proportion = number_cases/n_papers) %>% 
        ungroup() %>%
        group_by(md_id) %>%
        mutate(total_cases = sum(number_cases),
               proportion_sum = sum(proportion),
               proportion_lbl = paste0(round(proportion_sum*100,1), "%")) %>% 
        ungroup() %>%
        arrange(desc(proportion_sum), md_id)

# convert to factor to retain sorted order in plot.
data_kp_barchart$md_desc <- factor(data_kp_barchart$md_desc, levels=unique(data_kp_barchart$md_desc))  

data_kp_barchart$val_asstype <- fct_relevel(data_kp_barchart$val_asstype, 
                                            c("NO", "USABILITY/UX", "EFFECT AND USABILITY/UX", "EFFECT"))
                                            
# Not run
# display.brewer.all()
# display.brewer.pal(n = 6, name = "PRGn")
# brewer.pal(n = 6, name = "PRGn")[2:5]

# divergent palette instead of categorical (Set2). Get rid of edge values to avoid sharp contrast
pal <- brewer.pal(n = nlevels(data_kp_barchart$val_asstype)+2, name = "PRGn")[2:5]
pal <- c("#762A83", "#D9F0D3", "#7FBF7B", "#1B7837")

kp_barchart <- 
    data_kp_barchart %>%
      ggplot(aes(x=md_desc, y=number_cases, label=number_cases)) + #, fill=val_ass, group= val_ass)) +
        geom_bar(stat="identity", aes(fill=val_asstype), position = position_stack(reverse = T)) +
        geom_text(aes(label=number_cases, group=val_asstype), size=2, nudge_y=0.2) +
        labs(title=paste0("Distribution of papers per mental disorder (N=",n_papers,")"),
             x="Mental disorders", 
             y="Number of cases", 
             caption="Source: authors") + 
        coord_flip() +
        guides(fill=guide_legend(title="Assessment Type")) +  # modify legend title
        # scale_fill_brewer(palette = pal) + # Set2
        scale_fill_manual(values = pal) + 
        scale_y_continuous(expand=c(0,0), breaks=seq(0, 22, by=2), limits=c(0, 22)) +
        theme_minimal()  +
        # Legend: Top-Right Inside the Plot") 
        theme(legend.title = element_text(size=11), 
              legend.justification = c('right', 'top'),
              legend.position=c(0.95, 0.95),  
              #legend.background = element_blank(),
              legend.background = element_rect(color = "darkgray", size = 0.5, linetype ="solid"),
              legend.key = element_blank()) +
        # Change the line type and color of axis lines
        theme(axis.line = element_line(colour = "darkgray", size = 0.5, linetype = "solid")) +
        theme(panel.grid.major = element_blank()) + 
        theme(panel.grid.minor = element_blank()) +
        theme(panel.background = element_blank()) +
        theme(plot.margin=unit(rep(20, 4), "pt"))

kp_barchart
kp_file_name <- "fig2_barchart_stack.png"
ggsave(plot = kp_barchart, filename = kp_file_name, device = "png", path = here::here("figs"),
    scale = 1, width = 20, height = 12, units = "cm", dpi = 600)

```


### Figure 3. Distribution of papers per mental disorder and assessment type

Proportional (stacked) barchart: Distribution of papers per mental disorders, colored by assessment type. Note that we draw two main colors in the legend: purple represents no assessment at all, the range of greens denotes distinct types of assessment. Total percentatge per mental disorder is given at the end of each bar (white circle)

```{r fig3_barchart, echo=FALSE,dpi=600,fig.width=10,fig.asp=0.65}
cols <- c("md", "md_id", "md_desc", "val_asstype")

data_plot_barchart <- 
    all_data %>%
    select(cols)

data_plot_barchart <- 
    data_plot_barchart %>% 
        group_by(md_id, md_desc, val_asstype) %>%  # first create counts for each group
        summarise(number_cases = n()) %>%
        mutate(proportion = number_cases/n_papers) %>% 
        ungroup() %>%
        group_by(md_id) %>%
        mutate(total_cases = sum(number_cases),
               proportion_sum = sum(proportion),
               proportion_lbl = paste0(round(proportion_sum*100,1), "%")) %>% 
        ungroup() %>%
        mutate(lbl = paste0(round(number_cases/total_cases*100,1), "%")) %>% 
        arrange(desc(proportion_sum), md_id)

# convert to factor to retain sorted order in plot.
data_plot_barchart$md_desc <- factor(data_plot_barchart$md_desc, levels=unique(data_plot_barchart$md_desc))  

data_plot_barchart$val_asstype <- fct_relevel(data_plot_barchart$val_asstype, 
                                            c("NO ASSESSMENT", "USABILITY/UX", "EFFECT AND USABILITY/UX", "EFFECT"))
                                            

# Not run
# display.brewer.all()
# display.brewer.pal(n = 7, name = "PRGn")
# brewer.pal(n = 7, name = "PRGn")
# divergent palette instead of categorical (Set2). Get rid of edge values to avoid sharp contrast
#pal <- brewer.pal(n = nlevels(data_plot3_barchart$val_asstype), name = "PRGn")
pal <- c("NO ASSESSMENT"="#AF8DC3", "USABILITY/UX"="#D9F0D3", "EFFECT AND USABILITY/UX"="#7FBF7B", "EFFECT"="#1B7837")

lbls <- distinct(data_plot_barchart, md_desc, proportion_sum, proportion_lbl)

top_proportion <- sum(lbls[1:6, "proportion_sum"]) 
top_lbl <- paste0(round(top_proportion*100,1), "%")

plot_barchart <- 
    data_plot_barchart %>%
      ggplot(aes(x=md_desc, y=proportion, fill=val_asstype)) + 
        geom_bar(stat="identity") +
        labs(#title="Distribution per mental disorder and assessment type", 
             #subtitle = "Total percentatge per mental disorder within each point",
             x="Mental disorders", 
             y="# of papers and total percentage", 
             caption="Source: authors") + 
        # geom_segment(aes(x=md_desc, y=0, xend=md_desc, yend=proportion_sum), color="white") + # grey50
        geom_point(aes(y=proportion_sum), size=6, color="white", show.legend = F) +  
        # geom_text(aes(label=number_cases), size=2.5, position=position_stack(vjust = 0.5)) +
        geom_text(aes(label=number_cases), size=2.5, position=position_stack(vjust = 0.4)) +
        # Percentatge inside point
        annotate("text", x = lbls$md_desc, y = lbls$proportion_sum,
                 label = lbls$proportion_lbl, color = "black", size=2, hjust = 0.4, vjust = 0.2) +
        # Arrow to indidate  Top6 mental disorders 
        annotate("text", x = "Schizophrenia spectrum and\n other psychotic disorders", y = .16,
                 label = top_lbl, color = "black", size = 3, hjust = -0.1, vjust = 1.2) +
        geom_segment(aes(x = "Schizophrenia spectrum and\n other psychotic disorders", 
                         xend = "Substance-related and\n addictive disorders", 
                         y = .18, 
                         yend = .18),
                         arrow = arrow(length = unit(0.5,"cm")), color = "black") +
        geom_segment(aes(x="Schizophrenia spectrum and\n other psychotic disorders", 
                         y=0.11, 
                         xend="Schizophrenia spectrum and\n other psychotic disorders", 
                         yend=0.18), color="black") +
        coord_flip() +
        scale_fill_manual(name="Assessment Type", values = pal) + 
        scale_y_continuous(expand=c(0,0), labels=scales::percent_format(accuracy = 1), breaks=seq(0, 0.21, by=0.02), limits=c(0, 0.21)) +
        # Which legend to show
        guides(fill=guide_legend(title="Assessment Type", nrow=2)) + # modify legend title
        theme_minimal()  +
        theme(legend.title = element_text(size=11),
              legend.position = "bottom",
              # legend.justification = c('right', 'top'),
              # legend.position=c(0.95, 0.95),
              legend.background = element_rect(color = "darkgray", size = 0.5, linetype ="solid"),
              legend.key = element_blank()) +
        # Change the line type and color of axis lines
        theme(axis.line = element_line(colour = "darkgray", size = 0.5, linetype = "solid")) +
        theme(panel.grid.major = element_blank()) + 
        theme(panel.grid.minor = element_blank()) +
        theme(panel.background = element_blank()) +
        theme(plot.margin=unit(rep(20, 4), "pt"))

# plot_barchart


data_plot_piechart <-
    data_plot_barchart %>%
    group_by(val_asstype) %>%
    summarise(total_asstype = sum(number_cases)) %>%
    mutate(lbl = paste0(round(total_asstype/n_papers*100,1), "%"),
           cumulative= cumsum(total_asstype),
           midpoint = cumulative-total_asstype/2) %>% 
    arrange(desc(total_asstype))

data_plot_piechart$val_asstype <-  fct_relevel(data_plot_piechart$val_asstype, 
                                               c("EFFECT", "USABILITY/UX", "NO ASSESSMENT", "EFFECT AND USABILITY/UX"))
plot_piechart <- 
    data_plot_piechart %>%
    ggplot(aes(x="", y=total_asstype, fill=val_asstype)) +
    geom_bar(width=1, stat = "identity") +
    coord_polar(theta="y", start=0, direction = 1) +
    geom_text(aes(y=midpoint, label=lbl), size=3, show.legend = F) +
    scale_fill_manual(name="Assessment Type", values = pal) + 
    # Which legend to show
    guides(fill="none") +
    theme_minimal() +
    theme(legend.title = element_text(size=9)) +
    theme(axis.text = element_blank(),
          axis.ticks = element_blank(),
          panel.grid = element_blank()) +
    theme(panel.border = element_rect(fill=NA, colour = "darkgray", size=0.5)) +
    labs(x=NULL, y=NULL, title="Accumulated results [%]")

# plot_piechart


plot_dist_md <-
    ggdraw() +
    draw_plot(plot_barchart) +
    draw_plot(plot_piechart, 0.55, 0.55, 0.40, 0.40)

plot_dist_md

        
plot_dist_md_file_name <- "fig3_dist_md.png"
ggsave(plot = plot_dist_md, filename = plot_dist_md_file_name, device = "png", path = here::here("figs"),
     scale = 1, width = 22, height = 18, units = "cm", dpi = 600)


```



Distribution of types of assessments per mental disorders

```{r stats_assesstype_md, echo=FALSE}

data_plot_barchart %>%
    # arrange(desc(md_desc)) %>%
    select(`Mental Disorder` = md_desc,
           `Type of assessment` = val_asstype,
           `Percentage`= lbl) %>%
    kable(formt="html", escape = T, booktabs = TRUE) %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
    column_spec(1, bold = T) %>%
    collapse_rows(columns = 1, valign = "top")
```




```{r echo=FALSE}
# TODO https://stackoverflow.com/questions/45055661/combine-grouped-and-stacked-bar-graph-in-r thanks
#- Add a new column (factor): No is value A, thre rest thre are B
#- use facet_wrap() over this new factor.  
# cols <- c("md", "md_id", "md_desc", "val_asstype", "val_ass")
# 
# data_kp_barchart <- 
#     all_data %>%
#     select(cols)
# 
# data_kp_barchart$val_asstype <- fct_relevel(data_kp_barchart$val_asstype, c("NO", "OTHERS", "EFFICACY AND OTHERS", "EFFICACY"))
# 
# data_kp_barchart <- 
#     data_kp_barchart %>% 
#         group_by(md_id, md_desc, val_asstype, val_ass) %>%  # first create counts for each group
#         summarise(number_cases = n()) %>%
#         mutate(proportion = number_cases/n_papers) %>% 
#         ungroup() %>%
#         group_by(md_id) %>%
#         mutate(total_cases = sum(number_cases),
#                proportion_sum = sum(proportion),
#                proportion_lbl = paste0(round(proportion_sum*100,1), "%")) %>% 
#         ungroup() %>%
#         arrange(desc(proportion_sum), md_id)
# 
# # convert to factor to retain sorted order in plot.
# data_kp_barchart$md_desc <- factor(data_kp_barchart$md_desc, levels=unique(data_kp_barchart$md_desc))  
# 
# kp_barchart <- 
#     data_kp_barchart %>%
#     ggplot(aes(x=val_ass, y=proportion)) + 
#     geom_bar(stat="identity", aes(fill=val_asstype), position="stack") + 
#         # Uncomment  for dodge barchart, single (option C) 
#         #geom_bar(stat="identity", aes(fill=val_asstype), position = position_dodge(preserve = "total")) + 
#     facet_wrap(~md_desc, ncol = 1) + theme(panel.spacing = unit(0, "lines")) +
#     coord_flip()

```

\newpage

### Figure 4. Distribution top mental disorders per year

Linechart: Distribution of papers (top6 mental disorders) per year.


```{r fig4_linechart, echo=FALSE, dpi=600, fig.width=12, fig.height=14, fig.asp=0.65}
cols_top <- c("Depressive disorders", 
              "Anxiety disorders", 
              "Various disorders",
              "Trauma and\n stressor-related disorders",
              "Substance-related and\n addictive disorders",
              "Schizophrenia spectrum and\n other psychotic disorders")
top <- levels(all_data$md)[1:6]

data_plot_topmd <- 
    all_data %>%
      filter(md %in% top) %>%
      group_by(md_desc, year) %>%
      summarise(number_cases = n()) %>%
      ungroup() %>%
      mutate(md_desc = factor(md_desc)) %>%
      arrange(desc(number_cases))

#' Add mental disorders with zero cases
for (y in 2013:2018) {
    md_year <- filter(data_plot_topmd, year==y) %>% select(md_desc)
    md_dif <- setdiff(cols_top, md_year$md_desc)
    if (length(md_dif) > 0) {
        for (md in md_dif) {
            data_plot_topmd <- add_row(data_plot_topmd, md_desc=md, year=y, number_cases=0)
        }
    }
}


# https://www.r-graph-gallery.com/portfolio/ggplot2-package/
# https://ggplot2.tidyverse.org/reference/position_stack.html

data_plot_topmd$md_desc <- fct_relevel(data_plot_topmd$md_desc, cols_top)

brks <- levels(data_plot_topmd$md_desc) 
# n_colors = nlevels(data_top_byyear$md_desc)
# get_palette <- colorRampPalette(brewer.pal(9, "Set2"))

plot_topmd <-
    data_plot_topmd %>%
        ggplot(aes(x=year, y=number_cases, group=md_desc)) +
        geom_vline(aes(xintercept = 2017), color="lightgray", linetype = "dashed", size = 0.5) +
        annotate("rect", xmin = 2017, xmax = 2018, ymin = -Inf, ymax = +Inf, fill = "lightgray", alpha = 0.2) +
        geom_line(aes(color=md_desc), size=2.5, alpha=.4) +
        # geom_point(aes(color=md_desc), size=6, alpha=.6) +
        geom_point(shape=21, size=7, color="darkgray", fill="white") +
        # scale_color_manual(name="Mental disorders", values = get_palette(n_colors), breaks=brks) +
        labs(#title="Distribution top mental disorders per year", 
             #subtitle = paste0("Top mental disorders (", top_lbl,")"),
             x="Year", 
             y="# of papers", 
             caption="Source: authors") + 
        scale_color_brewer(name="Mental disorders", palette="Set2", breaks=brks) +
        # geom_text(aes(label = number_cases), color= "white", size=3) +
        geom_text(aes(label = number_cases), color= "black", size=3) +
        scale_y_continuous(breaks=seq(0,8,by=1)) +
        theme_minimal() +
        # Legend: Top-Right Inside the Plot") 
        theme(legend.justification = c('left', 'top'),
              legend.position=c(0.05, 0.95),  
              #legend.background = element_blank(),
              legend.background = element_rect(color = "darkgray", size = 0.5, linetype ="solid"),
              legend.key = element_blank()) +
        theme(panel.grid.major = element_blank()) + 
        theme(panel.grid.minor = element_blank()) +
        theme(panel.background = element_blank()) +
        theme(plot.margin=unit(rep(20, 4), "pt")) +
        # Change the line type and color of axis lines
        theme(axis.line = element_line(colour = "darkgray", size = 0.5, linetype = "solid"))

plot_topmd
plot_file_name <- "fig4_linechart.png"
ggsave(plot = plot_topmd, filename = plot_file_name, device = "png", path = here::here("figs"),
    scale = 1, width = 20, height = 18, units = "cm", dpi = 600) 


```

\newpage

### Table 1 (OUT)

Table (Example 1): Distribution of papers (apps) per mental disorder.  _How many apps are related to each mental disorder?_ Per each mental disorder, assessment (yes/no) and year, we show the paper id and appname.


```{r tab1, echo=FALSE}

# library(formattable)

kp_file_name <- here::here("figs", "table1.html")
#' Example  1, verbose table
data_kp_apps <- 
    all_data %>%
    arrange(md_id, val_ass, year, id)

#' source: https://cran.r-project.org/web/packages/kableExtra/vignettes/awesome_table_in_html.html

# options(knitr.kable.NA = '-')
data_kp_apps %>%
    select(`Mental Disorder` = md,
           `Assessment` = val_ass,
           `Year` = year,
           `Paper id` = id,
           `App Name` = app_name) %>%
    kable(format="html", escape = T, booktabs = TRUE,
          caption =  paste0("Distribution of papers (apps) per mental disorder\n",
                            "'NA' is app not specified/available")) %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
    column_spec(1, bold = T) %>%
    collapse_rows(columns = 1:3, valign = "top") #%>%  
    # save_kable(file = kp_file_name, self_contained = T)

```

### Table 1 (IN, PRODUCTION)

Table (Example 2): _Compact_ distribution of papers (apps) per mental disorder, grouping the references per app. The mumber(s) in brackets next to the app name is the reference(s) in which the app is mentioned. 


```{r tab1_in, echo=FALSE}

kp_file_name <- here::here("figs", "table2.html")

unite_paper_ids <- function(mentaldisorder, appname) {
    if (!is.na(appname)) {
        all_data %>% 
            filter(md_desc == mentaldisorder & app_name==appname) %>%
            arrange(year) %>%
            select(id) %>%
            as_vector() %>%
            stringr::str_c(collapse = ";")    
    } else {
         all_data %>% 
            filter(md_desc == mentaldisorder & is.na(app_name)) %>%
            arrange(year) %>%
            select(id) %>%
            as_vector() %>%
            stringr::str_c(collapse = ";")  
    }
}

data_kp_apps2 <- 
    all_data %>%
    group_by(md_desc, app_name) %>%
    summarise(number_apps = n()) %>% 
    arrange(number_apps, md_desc)

data_kp_apps2 <- 
    data_kp_apps2 %>%
    add_column(ids = purrr::map2(data_kp_apps2$md_desc, data_kp_apps2$app_name, unite_paper_ids))

data_kp_apps2 <- 
    data_kp_apps2 %>%
    add_column(app_ids = paste0(data_kp_apps2$app_name, " (", data_kp_apps2$ids, ")"))

data_kp_apps2 <- 
    data_kp_apps2 %>%
    group_by(md_desc) %>%
    summarise(app_ids_merge = paste0(app_ids, collapse = ", ")) 

data_kp_apps2$md_desc <- factor(data_kp_apps2$md_desc, levels=md_all_ordered)  


# options(knitr.kable.NA = '-')
data_kp_apps2 %>%
    arrange(desc(md_desc)) %>%
    select(`Mental Disorder` = md_desc,
           `References by app` = app_ids_merge) %>%
    kable(formt="html", escape = T, booktabs = TRUE,    
          caption = paste0("Compact distribution of papers (apps) per mental disorder\n", 
                            "'NA' is app not specified/available")) %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
    column_spec(1, bold = T) %>%
    collapse_rows(columns = 1, valign = "top") #%>%  
    # save_kable(file = kp_file_name, self_contained = T)


```


### Figure 4 (IN/OUT?, DRAFT)

Circular barplot (Example 3): Each cell means one occurence of the app in a paper.

```{r key_plot_4_table3, echo=FALSE}

#' source: https://www.r-graph-gallery.com/297-circular-barplot-with-groups/

data_kp_apps3 <- 
    all_data %>%
    filter(as.integer(md_id) != 26) %>%
    group_by(app_name, md_desc) %>%
    summarise(number_apps = n()) %>% 
    arrange(md_desc, number_apps)

data_kp_apps3$app_name <- fct_explicit_na(data_kp_apps3$app_name, "Not App Available")
data_kp_apps3$id <- seq(1, nrow(data_kp_apps3))


# source: https://www.r-bloggers.com/how-to-expand-color-palette-with-ggplot-and-rcolorbrewer/
n_colors <- length(unique(data_kp_apps3$md_desc))
get_palette <- colorRampPalette(brewer.pal(8, "Set1"))


# Get the name and the y position of each label
label_data=data_kp_apps3
number_of_bar=nrow(label_data)
angle= 90 - 360 * (label_data$id-0.5)/number_of_bar     # I substract 0.5 because the letter must have the angle of the center of the bars. Not extreme right(1) or extreme left (0)
label_data$hjust<-ifelse(angle < -90, 1, 0)
label_data$angle<-ifelse(angle < -90, angle+180, angle)


kp_circularbarplot <- 
    ggplot(data_kp_apps3, aes(x=as.factor(id), y=number_apps, fill=md_desc)) +  
      geom_bar(stat="identity", alpha=0.5) +
      # Lmits of the plot: The negative value controls the size of the inner circle, the positive one is useful to add size over each bar
      ylim(-5,10) +
      scale_fill_manual(values = get_palette(n_colors), name="Mental disorders") +
      scale_color_manual(values = get_palette(n_colors)) +    
      theme_minimal() +
      theme(
        legend.position = "right",
        legend.title = element_blank(),
        legend.text = element_text(size=5),
        axis.text = element_blank(),
        axis.title = element_blank(),
        panel.grid = element_blank(),
        plot.margin = unit(rep(-1,4), "cm")
      ) +
      guides (fill = guide_legend(ncol=1)) +    
      coord_polar(start=0) + 
      geom_text(data=label_data, aes(x=id, y=number_apps, label=app_name, hjust=hjust, color=md_desc), 
                alpha=0.6, size=3, angle= label_data$angle, inherit.aes = FALSE, show.legend = FALSE ) +
      geom_hline(yintercept = seq(1:10), col = "white", lwd=0.5)

kp_circularbarplot

kp_file_name <- "fig4_circularbarplot.png"
ggsave(plot = kp_circularbarplot, filename = kp_file_name, device = "png", path = here::here("figs"),
    scale = 1, width = 25, height = 25, units = "cm", dpi = "print") #300


```

```{r echo=FALSE}

#' circlize, source: http://jokergoo.github.io/circlize/example/bi_directional.html
# library(circlize)
# 
# appnames <- unique(data_kp_apps3$app_name)
# fappnames <- factor(data_kp_apps3$app_name, levels = appnames)    
# 
# circos.clear()
# circos.initialize(factors = fappnames, x = appnames)
# 
# factors = appnames[1:4] #letters[1:4]
# circos.initialize(factors = factors, xlim = c(0, 1))
# circos.track(ylim = c(0, 1), panel.fun = function(x, y) {
#     circos.points(1:20/20, 1:20/20)
# })
# text(0, 0, "This is\nthe center", cex = 1.5)
# legend("bottomleft", pch = 1, legend = "This is the legend")
# title("This is the title")
# 
# 
# col_fun = colorRamp2(c(-2, 0, 2), c("green", "yellow", "red"))
# 
# circlize_plot = function() {
#     set.seed(12345)
#     fa <- appnames[1:10]
#     n <- length(fa)
#     circos.initialize(factors = fa, xlim = c(0, 1))
#     circos.track(ylim = c(0, 1), panel.fun = function(x, y) {
#         circos.points(runif(20), runif(20), cex = 0.5, pch = 16, col = 2)
#         circos.points(runif(20), runif(20), cex = 0.5, pch = 16, col = 3)
#     })
#     circos.track(ylim = c(0, 1), panel.fun = function(x, y) {
#         circos.lines(sort(runif(20)), runif(20), col = 4)
#         circos.lines(sort(runif(20)), runif(20), col = 5)
#     })
# 
#     for(i in n) {
#         circos.link(sample(fa, 1), sort(runif(10))[1:2], 
#                     sample(fa, 1), sort(runif(10))[1:2],
#                     col = add_transparency(col_fun(rnorm(1))))
#     }
#     circos.clear()
# }
# 
# circlize_plot()
# 
# 
# 
# set.seed(999)
# mat <- matrix(sample(18, 18), 3, 6) 
# rownames(mat) <- paste0("S", 1:3)
# colnames(mat) <- paste0("E", 1:6)
# mat
# 
# 
# df <- data.frame(from = rep(rownames(mat), times = ncol(mat)),
#     to = rep(colnames(mat), each = nrow(mat)),
#     value = as.vector(mat),
#     stringsAsFactors = FALSE)
# 
# df
# 
# 
# circos.par(start.degree = 90, track.margin = c(-0.1, 0.1), gap.degree = 4, points.overflow.warning = FALSE)
# chordDiagram(df)
# circos.clear()


```

\newpage

### Figure 5. Distribution of papers per mental disorder vs technology

Bubble plot: Distribution of papers per mental disorder and technology variables (sensor capabilities and features). Technology-related characteristics are ranked in each dimension.

In the following, some exploratory charts are shown on the way to reach the bubble plot, which is the last chart. None of the following charts are in production stage, only drafted. Please, do not pay much attention to the color palette and aesthetics yet.

```{r key_plot_5_sens, echo=FALSE, dpi=600, fig.width=12, fig.height=14, fig.asp=0.65}
# Sensory capabilities related to each mental disorder 
cols = c("id", "md", "md_id", "md_desc", 
         "sens_acc", "sens_gyr", "sens_gps", "sens_mic", "sens_cam",
         "os_ios", "os_and", "app_name",
         "type", "year")
cols_sens <- c("sens_acc", "sens_gyr", "sens_gps", "sens_mic", "sens_cam")

n_sens <- 
    all_data %>%
    select(cols_sens) %>%
    filter((sens_acc=="YES") | (sens_gyr=="YES") | (sens_gps=="YES") | 
              (sens_mic=="YES") | (sens_cam=="YES")) %>%
    nrow()

all_data %>%
    select(cols) %>%
    gather(cols_sens, key="tech_type", value="tech_value") %>%
    ggplot(aes(x=md_desc)) +
    geom_bar(stat="count", aes(fill=factor(tech_value))) +
    coord_flip() +
    facet_wrap(~tech_type)


```


`r percent(n_sens/n_papers)` of papers use **at least** a sensing capability (N=`r n_sens`). The use of the acc and gyr is residual; gps and mic are more significant, but in a low proportion: gps = `r percent(nrow(filter(all_data, sens_gps=="YES"))/n_papers)`, mic = `r percent(nrow(filter(all_data, sens_mic=="YES"))/n_papers)`, cam = `r percent(nrow(filter(all_data, sens_cam=="YES"))/n_papers)` . Note that some papers use both type of sensors, so the sum of percentages of gps, mic and cam exceeds the total percentage of papers that use **at least** a sensing capability.



```{r key_plot_5_feat, echo=FALSE,dpi=600, fig.width=12, fig.height=14, fig.asp=0.65}
# features related to each mental disorder 
cols = c("id", "md", "md_id", "md_desc", 
         "feat_use", "feat_promp", "feat_soc", "feat_hcp", "feat_learn", 
         "feat_prog", "feat_ca", "feat_ass", "feat_vr", "feat_ar", "feat_pers", "feat_game",
         "os_ios", "os_and", "app_name",
         "type", "year")

cols_feat = c("feat_use", "feat_promp", "feat_soc", "feat_hcp", "feat_learn", 
              "feat_prog", "feat_ca", "feat_ass", "feat_vr", "feat_ar", "feat_pers", "feat_game")
n_feat <- 
    all_data %>%
    select(cols_feat) %>%
    filter((feat_use=="YES") || (feat_promp=="YES") || (feat_soc=="YES") || (feat_hcp=="YES") || 
           (feat_learn=="YES") || (feat_prog=="YES") || (feat_ca=="YES") || (feat_ass=="YES") || 
           (feat_vr=="YES") || (feat_ar=="YES") || (feat_pers="YES") || (feat_game="YES"))  %>%
    nrow()

all_data %>%
    select(cols) %>%
    gather(cols_feat, key="tech_type", value="tech_value") %>%
    ggplot(aes(x=md_desc)) +
    geom_bar(stat="count", aes(fill=factor(tech_value))) +
    coord_flip() +
    facet_wrap(~tech_type)

```

`r percent(n_feat/n_papers)` of papers provide/offer/use **at least** a feature capability (N=`r n_feat`). 



```{r key_plot_5_anal, echo=FALSE,dpi=600, fig.width=12, fig.height=14, fig.asp=0.65}
# analytics support related to each mental disorder 
cols = c("id", "md", "md_id", "md_desc", 
         "anal_ml", "anal_beh", "anal_act", "anal_sp", 
         "os_ios", "os_and", "app_name",
         "type", "year")

cols_anal = c("anal_ml", "anal_beh", "anal_act", "anal_sp")
n_anal <- 
    all_data %>%
    select(cols_anal) %>%
    filter((anal_ml=="YES") | (anal_beh=="YES") | (anal_act=="YES") | (anal_sp=="YES"))  %>%
    nrow()

all_data %>%
    select(cols) %>%
    gather(cols_anal, key="tech_type", value="tech_value") %>%
    ggplot(aes(x=md_desc)) +
    geom_bar(stat="count", aes(fill=factor(tech_value))) +
    coord_flip() +
    facet_wrap(~tech_type)
```


`r percent(n_anal/n_papers)` of papers implement/use **at least** advanced analytics (N=`r n_anal`). 



```{r key_plot_5_sens_bubblechart, echo=FALSE, warning=FALSE, dpi=600, fig.width=12, fig.height=14, fig.asp=0.65}
cols = c("id", "md_id", "md_desc", 
         "sens_acc", "sens_gyr", "sens_gps", "sens_mic", "sens_cam",
         "app_name", "year")

cols_sens <- c("sens_acc", "sens_gyr", "sens_gps", "sens_mic", "sens_cam")
data_kp_sens <-
    all_data %>%
    select(cols) %>%
    gather(cols_sens, key="tech_type", value="tech_value") %>%
    mutate(cat = "Built-In sensors") %>%
    filter(tech_value == "YES") %>%
    group_by(md_desc, tech_type, cat) %>%
    summarise(number_cases = n()) %>%
    ungroup() # required to add_row() 


# For totals in final bubble plot
data_kp_sens_n <-
    data_kp_sens %>%
    group_by(tech_type) %>%
    summarise(n = sum(number_cases)) %>%
    arrange(desc(n))
                  

md_sens <- unique(data_kp_sens$md_desc)
md_dif <- setdiff(md_all_ordered, md_sens)
if (length(md_dif) > 0) {
    for (md in md_dif) {
        # Added "sens_mic" (or any other values) to avoid NA in the "tech_type" variable. Nothing is drawn in the plot
        data_kp_sens <- add_row(data_kp_sens, md_desc=md, tech_type="sens_mic", cat="Built-In sensors")
    }
}

data_kp_sens$md_desc <- fct_relevel(data_kp_sens$md_desc, levels=md_all_ordered)

data_kp_sens %>%
    ggplot(aes(x=md_desc, y=tech_type)) +
    geom_point(aes(colour=tech_type, size=number_cases), na.rm = TRUE) + 
    geom_text(aes(label=number_cases), size=3, na.rm = TRUE) +
    scale_size_area(max_size=10) +
    coord_flip()

```



```{r key_plot_5_feat_bubblechart, echo=FALSE, dpi=600, fig.width=12, fig.height=14, fig.asp=0.65}
cols = c("id", "md_id", "md_desc", 
         "feat_use", "feat_promp", "feat_soc", "feat_hcp", "feat_learn", 
         "feat_prog", "feat_ca", "feat_ass", "feat_vr", "feat_ar", "feat_pers", "feat_game",
         "app_name", "year")

cols_feat = c("feat_use", "feat_promp", "feat_soc", "feat_hcp", "feat_learn", 
              "feat_prog", "feat_ca", "feat_ass", "feat_vr", "feat_ar", "feat_pers", "feat_game")

data_kp_feat <- 
    all_data %>%
    select(cols) %>%
    gather(cols_feat, key="tech_type",value="tech_value") %>%
    mutate(cat = "Software features") %>%
    filter(tech_value == "YES") %>%
    group_by(md_desc, tech_type, cat)  %>%
    summarise(number_cases = n())  %>%
    ungroup() # required to add_row() 


# For totals in final bubble plot
data_kp_feat_n <-
    data_kp_feat %>%
    group_by(tech_type) %>%
    summarise(n = sum(number_cases)) %>%
    arrange(desc(n))
                  

md_feat <- unique(data_kp_feat$md_desc)
md_dif <- setdiff(md_all_ordered, md_feat)
if (length(md_feat) > 0) {
    for (md in md_dif) {
        # Added "feat_use" (or any value) to avoid NA in the "tech_type" variable. Nothing is drawn in the plot
        data_kp_feat <- add_row(data_kp_feat, md_desc=md, tech_type="feat_use", cat="Software features")
    }
}

data_kp_feat$md_desc <- factor(data_kp_feat$md_desc, levels=md_all_ordered)  

data_kp_feat %>%
    ggplot(aes(x=md_desc, y=tech_type)) +
    geom_point(aes(colour=tech_type, size=number_cases)) + 
    geom_text(aes(label=number_cases), size=3) +
    scale_size_area(max_size=15) +
    coord_flip()

```


```{r key_plot_5_anal_bubblechart, echo=FALSE, dpi=600, fig.width=12, fig.height=14, fig.asp=0.65}
cols = c("id", "md", "md_id", "md_desc", 
         "anal_ml", "anal_beh", "anal_act", "anal_sp", 
         "app_name", "year")

cols_anal = c("anal_ml", "anal_beh", "anal_act", "anal_sp")

data_kp_anal <- 
    all_data %>%
    select(cols) %>%
    gather(cols_anal, key="tech_type",value="tech_value") %>%
    mutate(cat = "Analytics") %>%
    filter(tech_value == "YES") %>%
    group_by(md_desc, tech_type, cat)  %>%
    summarise(number_cases = n())  %>%
    ungroup() # required to add_row() 

# For totals in final bubble plot
data_kp_anal_n <-
    data_kp_anal %>%
    group_by(tech_type) %>%
    summarise(n = sum(number_cases)) %>%
    arrange(desc(n))

md_anal <- unique(data_kp_anal$md_desc)
md_dif <- setdiff(md_all_ordered, md_anal)
if (length(md_anal) > 0) {
    for (md in md_dif) {
        # Added "anal_ml" (or any value) to avoid NA in the "tech_type" variable. Nothing is drawn in the plot
        data_kp_anal <- add_row(data_kp_anal, md_desc=md, tech_type="anal_ml", cat="Analytics")
    }
}


data_kp_anal$md_desc <- factor(data_kp_anal$md_desc, levels=md_all_ordered)  

data_kp_anal %>%
    ggplot(aes(x=md_desc, y=tech_type)) +
    geom_point(aes(colour=tech_type, size=number_cases), na.rm = TRUE) + 
    geom_text(aes(label=number_cases), size=3, na.rm = TRUE) +
    scale_size_area(max_size=15) +
    coord_flip()
```


This is the final bubble plot. 

```{r key_plot_5_bubblechart, echo=FALSE, dpi=600, fig.width=15, fig.height=14, fig.asp=0.65}

data_kp_all <-
    bind_rows(data_kp_feat, data_kp_sens, data_kp_anal)

data_kp_all$tech_type <- as_factor(data_kp_all$tech_type)
#' Replace existing factors levels for production
levels(data_kp_all$tech_type)[levels(data_kp_all$tech_type)=="feat_learn"] <- "Learning"
levels(data_kp_all$tech_type)[levels(data_kp_all$tech_type)=="feat_prog"] <- "Progress"
levels(data_kp_all$tech_type)[levels(data_kp_all$tech_type)=="feat_pers"] <- "Personalization"
levels(data_kp_all$tech_type)[levels(data_kp_all$tech_type)=="feat_ass"] <- "Assessment"
levels(data_kp_all$tech_type)[levels(data_kp_all$tech_type)=="feat_promp"] <- "Prompting"
levels(data_kp_all$tech_type)[levels(data_kp_all$tech_type)=="feat_hcp"] <- "Health Care Provider \nCommunication"
levels(data_kp_all$tech_type)[levels(data_kp_all$tech_type)=="feat_use"] <- "In-Situ Use"
levels(data_kp_all$tech_type)[levels(data_kp_all$tech_type)=="feat_soc"] <- "Social"
levels(data_kp_all$tech_type)[levels(data_kp_all$tech_type)=="feat_ca"] <- "Context-Awareness"
levels(data_kp_all$tech_type)[levels(data_kp_all$tech_type)=="feat_game"] <- "Game"
levels(data_kp_all$tech_type)[levels(data_kp_all$tech_type)=="feat_vr"] <- "Virtual Reality"
levels(data_kp_all$tech_type)[levels(data_kp_all$tech_type)=="feat_ar"] <- "Augmented Reality"

levels(data_kp_all$tech_type)[levels(data_kp_all$tech_type)=="sens_mic"] <- "Microphone"
levels(data_kp_all$tech_type)[levels(data_kp_all$tech_type)=="sens_gps"] <- "GPS"
levels(data_kp_all$tech_type)[levels(data_kp_all$tech_type)=="sens_cam"] <- "Camera"
levels(data_kp_all$tech_type)[levels(data_kp_all$tech_type)=="sens_acc"] <- "Accelerometer"
levels(data_kp_all$tech_type)[levels(data_kp_all$tech_type)=="sens_gyr"] <- "Gyroscope"

levels(data_kp_all$tech_type)[levels(data_kp_all$tech_type)=="anal_ml"] <- "Machine Learning"
levels(data_kp_all$tech_type)[levels(data_kp_all$tech_type)=="anal_act"] <- "Activity Analysis"
levels(data_kp_all$tech_type)[levels(data_kp_all$tech_type)=="anal_beh"] <- "Behavioral Analysis"
levels(data_kp_all$tech_type)[levels(data_kp_all$tech_type)=="anal_sp"] <- "Spatial Analysis"

cols_ordered <-  c("Learning", "Progress", "Personalization", "Assessment", "Prompting", "Health Care Provider \nCommunication", 
                   "In-Situ Use", "Social", "Context-Awareness", "Game",  "Virtual Reality", "Augmented Reality", 
                   "Microphone", "GPS", "Camera", "Accelerometer", "Gyroscope",  
                   "Machine Learning", "Activity Analysis", "Behavioral Analysis", "Spatial Analysis") 
dims_ordered <- c("Software features", "Built-In sensors", "Analytics")

data_kp_all$tech_type <- fct_relevel(data_kp_all$tech_type, cols_ordered)

data_kp_all_n <-
    bind_rows(data_kp_feat_n, data_kp_sens_n, data_kp_anal_n)

data_kp_all_n <-
    data_kp_all_n %>%
    mutate(tech_label = cols_ordered)


data_kp_all$cat <- factor(data_kp_all$cat)
data_kp_all$cat <- fct_relevel(data_kp_all$cat, dims_ordered)
brks <- levels(factor(data_kp_all$cat))

# Color per dimension: 
# Software features "#FC8D62"; Built-In sensors "#66C2A5"; Types of analyses "#8DA0CB"
lbls_colors <- 
    ifelse(unique(data_kp_all$tech_type) %in% c("Learning", "Progress", "Personalization", "Assessment", "Prompting", "Health Care Provider \nCommunication", "In-Situ Use", "Social", "Context-Awareness", "Game",  "Virtual Reality", "Augmented Reality"), "#FC8D62",
           ifelse(unique(data_kp_all$tech_type) %in% c("Microphone", "GPS", "Camera", "Accelerometer", "Gyroscope"), "#66C2A5",
           "#8DA0CB"))
               
kp_bubblechart <- 
    data_kp_all %>%
    ggplot(aes(x=md_desc, y=tech_type, colour=cat)) +
    geom_point(aes(size=number_cases), alpha=1, na.rm = TRUE)+#, show.legend = FALSE) +
    geom_text(aes(label=number_cases), colour="black", size=3, na.rm = TRUE) +
    scale_size_area(max_size=18) +
    coord_flip() +
    labs(#title="Mental disorders vs Technology", 
         #subtitle = "Technology-related characteristics are ranked in each dimension",
         x="Mental disorders", 
         y="Technology-related characteristics", 
         caption="Source: authors") + 
    scale_color_manual(name="Dimensions", breaks=brks,
                       values = c("Software features"="#FC8D62","Built-In sensors"="#66C2A5", "Analytics"="#8DA0CB")) +
    # Which legend to show
    guides(colour="legend",size = "none") +
    theme_minimal()  +
    theme(axis.text.x=element_text(angle=60, size=11, hjust=1, color=lbls_colors),
          axis.text.y=element_text(size=11)) +
    # Legend: Top-Right Inside the Plot") 
    # theme(legend.position = "right") +
    theme(legend.title = element_text(size=9),
          legend.justification = c('right', 'top'),
          legend.position=c(1, 0.90),
          #legend.background = element_blank(),
          legend.background = element_rect(color = "darkgray", size = 0.5, linetype ="solid"),
          legend.key = element_blank()) +
    # Change the line type and color of axis lines
    theme(axis.line = element_line(colour = "darkgray", size = 0.5, linetype = "solid")) +
    theme(panel.grid.major.x = element_blank()) + 
    theme(panel.grid.minor = element_blank()) +
    theme(panel.background = element_blank()) +
    theme(plot.margin=unit(rep(20, 4), "pt")) 

# Add annotations: total of columns

kp_bubblechart <-
    kp_bubblechart +
    annotate("rect", xmin = 14.40, xmax = 14.75, ymin = 0.5, ymax = 12.4, 
             fill = "#FC8D62", alpha = 0.6) +
    annotate("rect", xmin = 14.40, xmax = 14.75, ymin = 12.6, ymax = 17.4, 
             fill = "#66C2A5", alpha = 0.6) +
    annotate("rect", xmin = 14.40, xmax = 14.75, ymin = 17.6, ymax = 21.5, 
             fill = "#8DA0CB", alpha = 0.6)
    

for (i in 1:nrow(data_kp_all_n)) {
     kp_bubblechart <-
        kp_bubblechart +
         # annotate("text", x = "Personality disorders", y = data_kp_all_n$tech_label[i], label = data_kp_all_n$n[i],
         #      color = lbls_colors[i], fontface="bold", size=3, hjust = 0.4, vjust = -1.8)
         annotate("text", x = "Personality disorders", y = data_kp_all_n$tech_label[i], label = data_kp_all_n$n[i],
              color = "white", fontface="bold", size=3, hjust = 0.4, vjust = -3)
}

# Add rectangles to highlight group of bubbles
kp_bubblechart <-
    kp_bubblechart +
    annotate("rect", xmin = 0.5, xmax = 11.5, ymin = 0.5, ymax = 7.5, 
             fill = "lightgray", alpha = 0.2, linetype="dashed") +
    annotate("rect", xmin = 0.5, xmax = 5.5, ymin = 0.5, ymax = 9.5, 
             fill = "lightgray", alpha = 0.2)


kp_bubblechart


kp_file_name <- "fig5_bubble.png"
ggsave(plot = kp_bubblechart, filename = kp_file_name, device = "png", path = here::here("figs"),
    scale = 1, width = 40, height = 25, units = "cm", dpi = 600)



```


